---
title: "Summaries of EDI-survey responses"
author: "Patrick Bolger"
date: now
date-format: "D MMM YYYY, h:mm a"
execute: 
  echo: false
format: 
  html:
    toc: true
    toc-title: Contents
    toc-depth: 5
    embed-resources: true
    code-fold: true
    code-summary: "Show the code"
    theme: cerulean
    mainfont: arvo
    page-layout: full
    fig-width: 11
    fig-height: 8
    fig_retina: 1
editor: source
bibliography: grateful-refs-sumandvis.bib
csl: apa.csl
---


```{r getPackages}
#| output: false

# List the packages needed for this file
neededPackages <- 
  c(
    "dplyr",
    "purrr",
    "tidyr",
    "forcats",
    "sysfonts",
    "showtext",
    "sjPlot",
    "sjlabelled",
    "sjmisc",
    "DT",
    "knitr",
    "gtsummary",
    "xfun",
    "stringr",
    "flextable",
    "showtext",
    "cowplot",
    "renv",
    "cowplot",
    "GGally",
    "ggplot2",
    "systemfonts",
    "magrittr",
    "ggtext"
    #"ggeasy"
    )

# The code directly below installs R packages 
# Uncomment the code directly below if you 
# don't already have them installed.
#install.packages(neededPackages)

# The grateful package isn't available on CRAN, so it needs to be
# downloaded and installed directly from GitHub.
# Uncomment the code directly below in order to do so.
#install.packages("remotes"); library(remotes); remotes::install_github("Pakillo/grateful")

#Attach the packages
invisible(lapply(neededPackages, require, character.only=T))
library(grateful)

```


```{r getFontArvo}
#| output: false

## use *arvo* font throughout

## an active internet connection is required for this step

font_add_google("Arvo", "arvo")
showtext_auto()

```


```{r readTidiedData}
#| output: false

# source of data
# The data imported here was pre-processed in another *R* script.

# Read in the data that was saved as .rds output in tidyingAndFormatting.qmd
visMain <- readRDS("tidyLabeledSurveyData.rds")
              
```

# importFunctions

```{r importCustomFunctions}

source("themesAndFunctions.R")

```


# summaries

The variables are listed in rough order of the appearance in the survey. However, all items regarding a particular identity (e.g., *gender*) are presented together here, whereas the first three items are separated from the latter eight items in the survey itself.

The summaries are broadly categorised into three groups, each with its own main heading:

- *background*\
- *EDI issues*\
- *Code of Conduct* and *documentation*

Each participant saw the all of the *background* items on the survey, as well as the *code-of-conduct* items. For the *EDI issues*, everyone saw at least one of the questions, with the exception of *gender*, in which case everyone saw at least two. 

The one question that everyone saw had to do with whether they identified with, or was typically associated with, one of the EDI groups. In the case of *gender*, they simply indicated their gender (not whether they had a gender or not).

If they answered *yes* to that question, two more questions appeared. The first invited them to supply more specific information about their identify, but only if they wanted to. The second had to do with whether they felt that this particular identity had affected their interactions in the *PsychoPy*<sup>&reg;</sup> community.

This latter question determined whether participants saw a further eight questions regarding that particular identity. If they answered *yes*, they saw them. If they answered *no*, they did not. 

This has an important entailment: namely, although one may identify or be associated with a particular identity, that does not necessarily mean that that person felt that it had affected their interactions in the *PsychoPy*<sup>&reg;</sup> community. Indeed, there were many participants throughout the survey who felt that they belonged with a particular identity, but indicated that it had not affected their interactions with the *PsychoPy*<sup>&reg;</sup> community.

Recall that for the dimension of *gender*, everyone saw the  question concerning whether they felt that their interactions had suffered as a result of gender. This is because everyone has a gender identity, so there was no logical way of excluding anyone from seeing the subsequent community-interaction question.

Below are the full survey categories in more detail.

- background\
  - career status\
  - type of engagement with *PsychoPy*<sup>&reg;</sup>\
  - ways of contributing\
  - deterrents to contributing\
- EDI issues\
  - gender\
  - sexual orientation\
  - race and/or culture\
  - disability and/or neurodivergence\
  - language dominance\
- Code of Conduct and documentation\
  - awareness\
  - findability, searchability, & accessibility of documentation\
  - trust in enforcement

None of the questions here required responses. 

Each of the headings in the list above above is depicted below with a visualisation, followed by a verbal summary of that visualisation, and then statistics on central tendency in cases where there were any Likert items.

## EDI issues

The second group of items on the survey collected information about selected dimensions of equity, diversity, and inclusion, namely *gender*, *sexual orientation*, *race* and/or *culture*, *disability* and/or *neurodivergence*, and *language dominance*.

For each dimension, participants were asked if they identified with the dimension, or whether they thought that others would associate them with it, along with the optional opportunity to supply more information about their own specific identity along this dimension.

Crucially, they were also asked whether they felt that that identity or association had affected their interactions in the *PsychoPy*<sup>&reg;</sup> community. If they answered in the affirmative, they saw eight more questions related to this identity shortly thereafter in the survey.

These eight further questions fell into three categories in the manner shown below:

- ***Treatment by others***\
  - *negative perception*\
  - *need to hide identity*\
  - *dismissiveness towards contributions*\
  - *target of derisive comments*\
  - *target of microaggressions*\
- ***Self-regard***\
  - *self-doubt*\
  - *stereotype threat*\
- ***Isolation***\
  - *a desire to interact with others more like themselves*
  
Participants could agree or disagree with each of these statements using a `1`-`7` Likert scale, where `1` indicated *Strongly disagree* and a `7` indicated *Strongly agree*.

::: {.callout-note}
Note that on the `1`-`7` scale for each of the statements, the number `4` is directly in the middle of the scale, which can be interpreted as neither agreeing nor disagreeing. You will see that we set responses of `4` to the side of the respective stacked frequency barplots, in yellow.

Also, the barplots are sorted within each category (*treatment*, *self-regard*, and *isolation*) along descending frequency of agreement. That is, the topmost barplot within each category is the one with highest number of agreements, whereas the bottommost barplot within each category is the one with the highest number of disagreements.
:::
  
Summaries of the responses to these statements are provided below after the respective questions concerning their identity.

### gender

The first EDI category is *gender*. We present the responses to the issue of identity, followed by a table of descriptions (supplied by some of the participants). This is followed by whether the participant felt affected in the *PsychoPy*<sup>&reg;</sup> community by that identity. Finally, we summarise the participants responses to items listed under *treatment* (by others), *self-regard*, and *isolation*. 

#### identity

The sections directly below summarise, both visually and verbally, the answer to the following question:

>`r get_label(visMain$gender)`

##### visualisation

```{r plotGender}
#| label: gender-plot
#| fig-alt: "Barplot of responses to the following statement: 'Which gender do you identify most with?'"

visMain |> 
  select(gender) |> 
  ostFreqPlot(
    ostColour = ostBlue,
    sorting = "none"
  )

```

##### verbal summary

- *`r get_label(visMain$gender)`*\
  - Total responses: `r length(which(!is.na(visMain$gender)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$gender)))/nrow(visMain),3)*100`% of the total\
  - Those who selected *man*: `r length(which(visMain$gender == "man"))`, or `r round(length(which(visMain$gender == "man"))/length(which(!is.na(visMain$gender))),3)*100`%\
  - Those who selected *not listed*: `r length(which(visMain$gender == "not listed"))`, or `r round(length(which(visMain$gender == "not listed"))/length(which(!is.na(visMain$gender))),3)*100`%\
  - Those who selected *woman*: `r length(which(visMain$gender == "woman"))`, or `r round(length(which(visMain$gender == "woman"))/length(which(!is.na(visMain$gender))),3)*100`%

#### descriptions

The table directly below lists the answers supplied to the following question:

>`r get_label(visMain$genderDesc)`

```{r tableGenderDesc}
#| label: gender-desc-table
#| tbl-cap: Descriptions of gender identities volunteered by participants

visMain |> 
  count(genderDesc) |>
  arrange(desc(n)) |>
  datatable(
    class = 'cell-border stripe',
    colnames = c(
      "Feel free to describe your gender here (or not)",
      "count"
      ),
    options = list(
      columnDefs = list(
        list(
          targets = 1,
          render = JS(
            "function(data, type, row, meta) {",
            "return data === null ? 'NA' : data;",
            "}"
            )
          )
        )
      )
    )


```


---

#### felt affected

The sections directly below summarise, both visually and verbally, the answer to the following question:

>`r get_label(visMain$genderAffected)`

##### visualisation

```{r plotGenderAffected}
#| label: gender-affected-plot
#| fig-alt: "Barplot of responses to: 'Do you feel that your gender status has affected your interactions with the PsychoPy community or software ecosystem?'"

visMain |> 
  select(genderAffected) |> 
  ostFreqPlot(
    ostColour = ostOrange,
    sorting = "none"
  )

```

##### verbal summary

- *`r get_label(visMain$genderAffected)`*\
  - Total responses: `r length(which(!is.na(visMain$genderAffected)))` (out of `r nrow(visMain)`)  or `r round(length(which(!is.na(visMain$genderAffected)))/nrow(visMain),3)*100`% of the total\
  - Those who selected ***no***: `r length(which(visMain$genderAffected == 0))`, or `r round(length(which(visMain$genderAffected == 0))/length(which(!is.na(visMain$genderAffected))),3)*100`% of those who responded to this question.\
  - Those who selected ***yes***: `r length(which(visMain$genderAffected == 1))`, or `r round(length(which(visMain$genderAffected == 1))/length(which(!is.na(visMain$genderAffected))),3)*100`% of those who responded to this question.\

  
::: {.callout-important}
##### Important insight
This question regarding *gender* determined whether or not the participant saw the items regarding *treatment (by others)*, *self-regard*, and *isolation*.

- Of the **`r length(which(visMain$gender == "man"))`** participants who identified as men, **`r numbers_to_words(length(which(visMain$gender == "man" & visMain$genderAffected == 1)))`** responded ***yes*** to this question.\
- Of the **`r length(which(visMain$gender == "woman"))`** participants who identified as women, **`r numbers_to_words(length(which(visMain$gender == "woman" & visMain$genderAffected == 1)))`** responded ***yes*** to this question.\
- Of the **`r length(which(visMain$gender == "not listed"))`** participants who indicated their gender was not listed, **`r numbers_to_words(length(which(visMain$gender == "not listed" & visMain$genderAffected == 1)))`** responded ***yes*** to this question.
:::

---

#### treatment, self-regard, isolation

The following statements were seen only by the subset of participants noted above. Specifically, they were restricted to the **`r numbers_to_words(length(which(visMain$genderAffected==1)))`** who replied ***yes*** to the question asking them whether they had felt that their gender identity has affected their interactions with the *PsychoPy*<sup>&reg;</sup> community. 

The exact questions are listed in the verbal summary after the visualisation.

##### visualisation

```{r plotGenderLikert}
#| warning: false
#| label: gender-likert-plot
#| fig-alt: "Stacked frequency barplots of responses to several statements on gender, categorized into the following: treatment by others, self-regard, and isolation." 

visMain |> 
  select(genderNegPerc:genderOthersLikeMe) |> 
  stackedLikertGroups(likertTitle = "Gender")

```

##### verbal summary

Below, we describe the numbers in the figure above, but in the order in which the items appeared in the survey.

###### treatment by others

- *`r get_label(visMain$genderNegPerc)`*\
  - Total responses: `r length(which(!is.na(visMain$genderNegPerc)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$genderNegPerc)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$genderNegPerc == 1))+length(which(visMain$genderNegPerc == 2))+length(which(visMain$genderNegPerc == 3))`, or `r round((length(which(visMain$genderNegPerc == 1))+length(which(visMain$genderNegPerc == 2))+length(which(visMain$genderNegPerc == 3)))/length(which(!is.na(visMain$genderNegPerc))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$genderNegPerc == 4))`, or `r round(length(which(visMain$genderNegPerc == 4))/length(which(!is.na(visMain$genderNegPerc))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$genderNegPerc == 5))+length(which(visMain$genderNegPerc == 6))+length(which(visMain$genderNegPerc == 7))`, or `r round((length(which(visMain$genderNegPerc == 5))+length(which(visMain$genderNegPerc == 6))+length(which(visMain$genderNegPerc == 7)))/length(which(!is.na(visMain$genderNegPerc))),3)*100`%

- *`r get_label(visMain$genderHideID)`*\
  - Total responses: `r length(which(!is.na(visMain$genderHideID)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$genderHideID)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$genderHideID == 1))+length(which(visMain$genderHideID == 2))+length(which(visMain$genderHideID == 3))`, or `r round((length(which(visMain$genderHideID == 1))+length(which(visMain$genderHideID == 2))+length(which(visMain$genderHideID == 3)))/length(which(!is.na(visMain$genderHideID))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$genderHideID == 4))`, or `r round(length(which(visMain$genderHideID == 4))/length(which(!is.na(visMain$genderHideID))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$genderHideID == 5))+length(which(visMain$genderHideID == 6))+length(which(visMain$genderHideID == 7))`, or `r round((length(which(visMain$genderHideID == 5))+length(which(visMain$genderHideID == 6))+length(which(visMain$genderHideID == 7)))/length(which(!is.na(visMain$genderHideID))),3)*100`%
  
- *`r get_label(visMain$genderIgnored)`*\
  - Total responses: `r length(which(!is.na(visMain$genderIgnored)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$genderIgnored)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$genderIgnored == 1))+length(which(visMain$genderIgnored == 2))+length(which(visMain$genderIgnored == 3))`, or `r round((length(which(visMain$genderIgnored == 1))+length(which(visMain$genderIgnored == 2))+length(which(visMain$genderIgnored == 3)))/length(which(!is.na(visMain$genderIgnored))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$genderIgnored == 4))`, or `r round(length(which(visMain$genderIgnored == 4))/length(which(!is.na(visMain$genderIgnored))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$genderIgnored == 5))+length(which(visMain$genderIgnored == 6))+length(which(visMain$genderIgnored == 7))`, or `r round((length(which(visMain$genderIgnored == 5))+length(which(visMain$genderIgnored == 6))+length(which(visMain$genderIgnored == 7)))/length(which(!is.na(visMain$genderIgnored))),3)*100`%
  
- *`r get_label(visMain$genderDerisive)`*\
  - Total responses: `r length(which(!is.na(visMain$genderDerisive)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$genderDerisive)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$genderDerisive == 1))+length(which(visMain$genderDerisive == 2))+length(which(visMain$genderDerisive == 3))`, or `r round((length(which(visMain$genderDerisive == 1))+length(which(visMain$genderDerisive == 2))+length(which(visMain$genderDerisive == 3)))/length(which(!is.na(visMain$genderDerisive))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$genderDerisive == 4))`, or `r round(length(which(visMain$genderDerisive == 4))/length(which(!is.na(visMain$genderDerisive))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$genderDerisive == 5))+length(which(visMain$genderDerisive == 6))+length(which(visMain$genderDerisive == 7))`, or `r round((length(which(visMain$genderDerisive == 5))+length(which(visMain$genderDerisive == 6))+length(which(visMain$genderDerisive == 7)))/length(which(!is.na(visMain$genderDerisive))),3)*100`%
  
- *`r get_label(visMain$genderMicroaggressions)`*\
  - Total responses: `r length(which(!is.na(visMain$genderMicroaggressions)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$genderMicroaggressions)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$genderMicroaggressions == 1))+length(which(visMain$genderMicroaggressions == 2))+length(which(visMain$genderMicroaggressions == 3))`, or `r round((length(which(visMain$genderMicroaggressions == 1))+length(which(visMain$genderMicroaggressions == 2))+length(which(visMain$genderMicroaggressions == 3)))/length(which(!is.na(visMain$genderMicroaggressions))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$genderMicroaggressions == 4))`, or `r round(length(which(visMain$genderMicroaggressions == 4))/length(which(!is.na(visMain$genderMicroaggressions))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$genderMicroaggressions == 5))+length(which(visMain$genderMicroaggressions == 6))+length(which(visMain$genderMicroaggressions == 7))`, or `r round((length(which(visMain$genderMicroaggressions == 5))+length(which(visMain$genderMicroaggressions == 6))+length(which(visMain$genderMicroaggressions == 7)))/length(which(!is.na(visMain$genderMicroaggressions))),3)*100`%
  
###### self-regard

- *`r get_label(visMain$genderSelfDoubt)`*\
  - Total responses: `r length(which(!is.na(visMain$genderSelfDoubt)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$genderSelfDoubt)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$genderSelfDoubt == 1))+length(which(visMain$genderSelfDoubt == 2))+length(which(visMain$genderSelfDoubt == 3))`, or `r round((length(which(visMain$genderSelfDoubt == 1))+length(which(visMain$genderSelfDoubt == 2))+length(which(visMain$genderSelfDoubt == 3)))/length(which(!is.na(visMain$genderSelfDoubt))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$genderSelfDoubt == 4))`, or `r round(length(which(visMain$genderSelfDoubt == 4))/length(which(!is.na(visMain$genderSelfDoubt))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$genderSelfDoubt == 5))+length(which(visMain$genderSelfDoubt == 6))+length(which(visMain$genderSelfDoubt == 7))`, or `r round((length(which(visMain$genderSelfDoubt == 5))+length(which(visMain$genderSelfDoubt == 6))+length(which(visMain$genderSelfDoubt == 7)))/length(which(!is.na(visMain$genderSelfDoubt))),3)*100`%

- *`r get_label(visMain$genderStereotypeThreat)`*\
  - Total responses: `r length(which(!is.na(visMain$genderStereotypeThreat)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$genderStereotypeThreat)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$genderStereotypeThreat == 1))+length(which(visMain$genderStereotypeThreat == 2))+length(which(visMain$genderStereotypeThreat == 3))`, or `r round((length(which(visMain$genderStereotypeThreat == 1))+length(which(visMain$genderStereotypeThreat == 2))+length(which(visMain$genderStereotypeThreat == 3)))/length(which(!is.na(visMain$genderStereotypeThreat))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$genderStereotypeThreat == 4))`, or `r round(length(which(visMain$genderStereotypeThreat == 4))/length(which(!is.na(visMain$genderStereotypeThreat))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$genderStereotypeThreat == 5))+length(which(visMain$genderStereotypeThreat == 6))+length(which(visMain$genderStereotypeThreat == 7))`, or `r round((length(which(visMain$genderStereotypeThreat == 5))+length(which(visMain$genderStereotypeThreat == 6))+length(which(visMain$genderStereotypeThreat == 7)))/length(which(!is.na(visMain$genderStereotypeThreat))),3)*100`%
  
###### isolation
  
- *`r get_label(visMain$genderOthersLikeMe)`*\
  - Total responses: `r length(which(!is.na(visMain$genderOthersLikeMe)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$genderOthersLikeMe)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$genderOthersLikeMe == 1))+length(which(visMain$genderOthersLikeMe == 2))+length(which(visMain$genderOthersLikeMe == 3))`, or `r round((length(which(visMain$genderOthersLikeMe == 1))+length(which(visMain$genderOthersLikeMe == 2))+length(which(visMain$genderOthersLikeMe == 3)))/length(which(!is.na(visMain$genderOthersLikeMe))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$genderOthersLikeMe == 4))`, or `r round(length(which(visMain$genderOthersLikeMe == 4))/length(which(!is.na(visMain$genderOthersLikeMe))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$genderOthersLikeMe == 5))+length(which(visMain$genderOthersLikeMe == 6))+length(which(visMain$genderOthersLikeMe == 7))`, or `r round((length(which(visMain$genderOthersLikeMe == 5))+length(which(visMain$genderOthersLikeMe == 6))+length(which(visMain$genderOthersLikeMe == 7)))/length(which(!is.na(visMain$genderOthersLikeMe))),3)*100`%

##### central tendency

```{r tableOfGenderStats}
#| label: gender-stats-table
#| tbl-cap: "Statistics for responses to statements regarding gender"
#| output: asis

visMain |>
  select(genderNegPerc:genderOthersLikeMe) |>
  tableLikert(
    lowerBound = "1 = Strongly disagree",
    upperBound = "7 = Strongly agree"
  )

```

#### [some remarks]

-   This is a pretty small group, but something that stands out so far is that only one of them agreed with most of the statements, and there was only one statement where two of them agreed with it (*isolation*)\
- Of course, the other surprising thing was that none of the participants who indicated that their gender was *not listed* indicated that they felt that their gender had affected their interactions in the *PsychoPy*<sup>&reg;</sup> community. Yet two people who identified as men and three who identified as women did. Note that we don't really have a way of determining what proportion of those four were transgender.

---

### sexual orientation

The second EDI category is *sexual orientation*. As above, we present the responses to the issue of identity, followed by a table of descriptions (supplied by some of the participants). This is followed by whether the participant felt affected in the *PsychoPy*<sup>&reg;</sup> community by that identity. Finally, we summarise the participants responses to items listed under *treatment* (by others), *self-regard*, and *isolation*. 

#### identity

##### visualisation

```{r plotNonhetero}
#| label: nonhetero-plot
#| fig-alt: "Barplot of responses to the following: 'Do you, or might others who know you well, consider you somehow NOT to be part of the heterosexual community?'"

visMain |> 
  select(nonHeteroCommunity) |> 
  ostFreqPlot(
    ostColour = ostYellow,
    sorting = "none"
  )

```

##### verbal summary

Below, we describe the numbers in the figure above.

- *`r get_label(visMain$nonHeteroCommunity)`*\
  - Total responses: `r length(which(!is.na(visMain$nonHeteroCommunity)))` (out of `r nrow(visMain)`)  or `r round(length(which(!is.na(visMain$nonHeteroCommunity)))/nrow(visMain),3)*100`% of the total\
  - Those who selected ***no***: `r length(which(visMain$nonHeteroCommunity == 0))`, or `r round(length(which(visMain$nonHeteroCommunity == 0))/length(which(!is.na(visMain$nonHeteroCommunity))),3)*100`%\
  - Those who selected ***yes***: `r length(which(visMain$nonHeteroCommunity == 1))`, or `r round(length(which(visMain$nonHeteroCommunity == 1))/length(which(!is.na(visMain$nonHeteroCommunity))),3)*100`%


---

#### descriptions

If participants chose ***yes*** as an answer above, they were given the opportunity to describe their sexual identity, though doing so was optional. For those who did, the table below lists the descriptions they provided.

The question was as follows:

>`r get_label(visMain$nonHeteroDesc)`

```{r tableNonheteroDesc}
#| label: nonhetero-desc-table
#| tbl-cap: "Descriptions of sexual orientation volunteered by participants"

visMain |> 
  count(nonHeteroDesc) |>
  arrange(desc(n)) |>
  datatable(
    class = 'cell-border stripe',
    colnames = c(
      "Feel free to describe your sexual orientation here (or not)",
      "count"
      ),
    options = list(
      columnDefs = list(
        list(
          targets = 1,
          render = JS(
            "function(data, type, row, meta) {",
            "return data === null ? 'NA' : data;",
            "}"
            )
          )
        )
      )
    )

```

---

#### felt affected

The sections directly below summarise, both visually and verbally, the answer to the following question:

>`r get_label(visMain$nonHeteroAffected)`

##### visualisation

```{r plotNonheteroAffected}
#| label: nonhetero-affected-plot
#| fig-alt: "Barplot of responses to the following: 'Do you feel that your sexual orientation has affected your interactions with the PsychoPy community...?'"

visMain |> 
  select(nonHeteroAffected) |> 
  ostFreqPlot(
    ostColour = ostBlue,
    sorting = "none"
  )

```

##### verbal summary

Below, we describe the numbers in the figure above.

- *`r get_label(visMain$nonHeteroAffected)`*\
  - Total responses: `r length(which(!is.na(visMain$nonHeteroAffected)))` (out of `r nrow(visMain)`)  or `r round(length(which(!is.na(visMain$nonHeteroAffected)))/nrow(visMain),3)*100`% of the total\
  - Those who selected ***no***: `r length(which(visMain$nonHeteroAffected == 0))`, or `r round(length(which(visMain$nonHeteroAffected == 0))/length(which(!is.na(visMain$nonHeteroAffected))),3)*100`% of those who responded to this question..\
  - Those who selected ***yes***: `r length(which(visMain$nonHeteroAffected == 1))`, or `r round(length(which(visMain$nonHeteroAffected == 1))/length(which(!is.na(visMain$nonHeteroAffected))),3)*100`% of those who responded to this question..\
    
::: {.callout-important}
##### Important insight
This question regarding *sexual orientation* determined whether or not the participant saw the items regarding *treatment (by others)*, *self-regard*, and *isolation*.

The `r numbers_to_words(length(which(visMain$nonHeteroAffected==1)))` ***yes*** response here comprises `r round(length(which(visMain$nonHeteroAffected==1))/length(which(visMain$nonHeteroCommunity==1)),3)*100`% of the `r length(which(visMain$nonHeteroCommunity==1))` who identified with a sexual orientation other than heterosexuality. In contrast, the `r length(which(visMain$nonHeteroAffected==0))` ***no*** responses here comprise `r round(length(which(visMain$nonHeteroAffected==0))/length(which(visMain$nonHeteroCommunity==1)),3)*100`%
:::

<!-- In the callout box above, there is currently (23 Feb 2023) only one YES response. This oddity forces a singular subject-verb agreement issue ("...***yes*** response here comprises...") that would disappear ("...***yes*** responses here comprise...") if this number increased at all. So this needs to be watched. This could be fixed with some conditional R code, but would be quite tedious. It's easier just to watch for a change. -->

---

#### treatment, self-regard, isolation

The following statements were seen only by the subset of participants noted above. Specifically, they were restricted to the **`r numbers_to_words(length(which(visMain$nonHeteroAffected==1)))`** who replied ***yes*** to the question asking them whether they had felt that their sexual orientation has affected their interactions with the *PsychoPy*<sup>&reg;</sup> community.

The exact questions are listed in the verbal summary after the visualisation.

##### visualisation

```{r plotNonheteroLikert}
#| warning: false
#| label: nonhetero-likert-plot
#| fig-alt: "Stacked frequency barplots of responses to several statements on sexuality, categorized into the following: treatment by others, self-regard, and isolation." 

visMain |>
  select(nonHeteroNegPerc:nonHeteroOthersLikeMe) |> 
  stackedLikertGroups(likertTitle = "Non-heterosexuality")

```

##### verbal summary

Below, we describe the numbers in the figure above, but in the order in which the items appeared in the survey.

###### treatment by others

- *`r get_label(visMain$nonHeteroNegPerc)`*\
  - Total responses: `r length(which(!is.na(visMain$nonHeteroNegPerc)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$nonHeteroNegPerc)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$nonHeteroNegPerc == 1))+length(which(visMain$nonHeteroNegPerc == 2))+length(which(visMain$nonHeteroNegPerc == 3))`, or `r round((length(which(visMain$nonHeteroNegPerc == 1))+length(which(visMain$nonHeteroNegPerc == 2))+length(which(visMain$nonHeteroNegPerc == 3)))/length(which(!is.na(visMain$nonHeteroNegPerc))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$nonHeteroNegPerc == 4))`, or `r round(length(which(visMain$nonHeteroNegPerc == 4))/length(which(!is.na(visMain$nonHeteroNegPerc))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$nonHeteroNegPerc == 5))+length(which(visMain$nonHeteroNegPerc == 6))+length(which(visMain$nonHeteroNegPerc == 7))`, or `r round((length(which(visMain$nonHeteroNegPerc == 5))+length(which(visMain$nonHeteroNegPerc == 6))+length(which(visMain$nonHeteroNegPerc == 7)))/length(which(!is.na(visMain$nonHeteroNegPerc))),3)*100`%

- *`r get_label(visMain$nonHeteroHideID)`*\
  - Total responses: `r length(which(!is.na(visMain$nonHeteroHideID)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$nonHeteroHideID)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$nonHeteroHideID == 1))+length(which(visMain$nonHeteroHideID == 2))+length(which(visMain$nonHeteroHideID == 3))`, or `r round((length(which(visMain$nonHeteroHideID == 1))+length(which(visMain$nonHeteroHideID == 2))+length(which(visMain$nonHeteroHideID == 3)))/length(which(!is.na(visMain$nonHeteroHideID))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$nonHeteroHideID == 4))`, or `r round(length(which(visMain$nonHeteroHideID == 4))/length(which(!is.na(visMain$nonHeteroHideID))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$nonHeteroHideID == 5))+length(which(visMain$nonHeteroHideID == 6))+length(which(visMain$nonHeteroHideID == 7))`, or `r round((length(which(visMain$nonHeteroHideID == 5))+length(which(visMain$nonHeteroHideID == 6))+length(which(visMain$nonHeteroHideID == 7)))/length(which(!is.na(visMain$nonHeteroHideID))),3)*100`%
  
- *`r get_label(visMain$nonHeteroIgnored)`*\
  - Total responses: `r length(which(!is.na(visMain$nonHeteroIgnored)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$nonHeteroIgnored)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$nonHeteroIgnored == 1))+length(which(visMain$nonHeteroIgnored == 2))+length(which(visMain$nonHeteroIgnored == 3))`, or `r round((length(which(visMain$nonHeteroIgnored == 1))+length(which(visMain$nonHeteroIgnored == 2))+length(which(visMain$nonHeteroIgnored == 3)))/length(which(!is.na(visMain$nonHeteroIgnored))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$nonHeteroIgnored == 4))`, or `r round(length(which(visMain$nonHeteroIgnored == 4))/length(which(!is.na(visMain$nonHeteroIgnored))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$nonHeteroIgnored == 5))+length(which(visMain$nonHeteroIgnored == 6))+length(which(visMain$nonHeteroIgnored == 7))`, or `r round((length(which(visMain$nonHeteroIgnored == 5))+length(which(visMain$nonHeteroIgnored == 6))+length(which(visMain$nonHeteroIgnored == 7)))/length(which(!is.na(visMain$nonHeteroIgnored))),3)*100`%
  
- *`r get_label(visMain$nonHeteroDerisive)`*\
  - Total responses: `r length(which(!is.na(visMain$nonHeteroDerisive)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$nonHeteroDerisive)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$nonHeteroDerisive == 1))+length(which(visMain$nonHeteroDerisive == 2))+length(which(visMain$nonHeteroDerisive == 3))`, or `r round((length(which(visMain$nonHeteroDerisive == 1))+length(which(visMain$nonHeteroDerisive == 2))+length(which(visMain$nonHeteroDerisive == 3)))/length(which(!is.na(visMain$nonHeteroDerisive))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$nonHeteroDerisive == 4))`, or `r round(length(which(visMain$nonHeteroDerisive == 4))/length(which(!is.na(visMain$nonHeteroDerisive))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$nonHeteroDerisive == 5))+length(which(visMain$nonHeteroDerisive == 6))+length(which(visMain$nonHeteroDerisive == 7))`, or `r round((length(which(visMain$nonHeteroDerisive == 5))+length(which(visMain$nonHeteroDerisive == 6))+length(which(visMain$nonHeteroDerisive == 7)))/length(which(!is.na(visMain$nonHeteroDerisive))),3)*100`%
  
- *`r get_label(visMain$nonHeteroMicroaggressions)`*\
  - Total responses: `r length(which(!is.na(visMain$nonHeteroMicroaggressions)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$nonHeteroMicroaggressions)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$nonHeteroMicroaggressions == 1))+length(which(visMain$nonHeteroMicroaggressions == 2))+length(which(visMain$nonHeteroMicroaggressions == 3))`, or `r round((length(which(visMain$nonHeteroMicroaggressions == 1))+length(which(visMain$nonHeteroMicroaggressions == 2))+length(which(visMain$nonHeteroMicroaggressions == 3)))/length(which(!is.na(visMain$nonHeteroMicroaggressions))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$nonHeteroMicroaggressions == 4))`, or `r round(length(which(visMain$nonHeteroMicroaggressions == 4))/length(which(!is.na(visMain$nonHeteroMicroaggressions))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$nonHeteroMicroaggressions == 5))+length(which(visMain$nonHeteroMicroaggressions == 6))+length(which(visMain$nonHeteroMicroaggressions == 7))`, or `r round((length(which(visMain$nonHeteroMicroaggressions == 5))+length(which(visMain$nonHeteroMicroaggressions == 6))+length(which(visMain$nonHeteroMicroaggressions == 7)))/length(which(!is.na(visMain$nonHeteroMicroaggressions))),3)*100`%
  
###### self-regard

- *`r get_label(visMain$nonHeteroSelfDoubt)`*\
  - Total responses: `r length(which(!is.na(visMain$nonHeteroSelfDoubt)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$nonHeteroSelfDoubt)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$nonHeteroSelfDoubt == 1))+length(which(visMain$nonHeteroSelfDoubt == 2))+length(which(visMain$nonHeteroSelfDoubt == 3))`, or `r round((length(which(visMain$nonHeteroSelfDoubt == 1))+length(which(visMain$nonHeteroSelfDoubt == 2))+length(which(visMain$nonHeteroSelfDoubt == 3)))/length(which(!is.na(visMain$nonHeteroSelfDoubt))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$nonHeteroSelfDoubt == 4))`, or `r round(length(which(visMain$nonHeteroSelfDoubt == 4))/length(which(!is.na(visMain$nonHeteroSelfDoubt))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$nonHeteroSelfDoubt == 5))+length(which(visMain$nonHeteroSelfDoubt == 6))+length(which(visMain$nonHeteroSelfDoubt == 7))`, or `r round((length(which(visMain$nonHeteroSelfDoubt == 5))+length(which(visMain$nonHeteroSelfDoubt == 6))+length(which(visMain$nonHeteroSelfDoubt == 7)))/length(which(!is.na(visMain$nonHeteroSelfDoubt))),3)*100`%

- *`r get_label(visMain$nonHeteroStereotypeThreat)`*\
  - Total responses: `r length(which(!is.na(visMain$nonHeteroStereotypeThreat)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$nonHeteroStereotypeThreat)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$nonHeteroStereotypeThreat == 1))+length(which(visMain$nonHeteroStereotypeThreat == 2))+length(which(visMain$nonHeteroStereotypeThreat == 3))`, or `r round((length(which(visMain$nonHeteroStereotypeThreat == 1))+length(which(visMain$nonHeteroStereotypeThreat == 2))+length(which(visMain$nonHeteroStereotypeThreat == 3)))/length(which(!is.na(visMain$nonHeteroStereotypeThreat))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$nonHeteroStereotypeThreat == 4))`, or `r round(length(which(visMain$nonHeteroStereotypeThreat == 4))/length(which(!is.na(visMain$nonHeteroStereotypeThreat))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$nonHeteroStereotypeThreat == 5))+length(which(visMain$nonHeteroStereotypeThreat == 6))+length(which(visMain$nonHeteroStereotypeThreat == 7))`, or `r round((length(which(visMain$nonHeteroStereotypeThreat == 5))+length(which(visMain$nonHeteroStereotypeThreat == 6))+length(which(visMain$nonHeteroStereotypeThreat == 7)))/length(which(!is.na(visMain$nonHeteroStereotypeThreat))),3)*100`%
  
###### isolation
  
- *`r get_label(visMain$nonHeteroOthersLikeMe)`*\
  - Total responses: `r length(which(!is.na(visMain$nonHeteroOthersLikeMe)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$nonHeteroOthersLikeMe)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$nonHeteroOthersLikeMe == 1))+length(which(visMain$nonHeteroOthersLikeMe == 2))+length(which(visMain$nonHeteroOthersLikeMe == 3))`, or `r round((length(which(visMain$nonHeteroOthersLikeMe == 1))+length(which(visMain$nonHeteroOthersLikeMe == 2))+length(which(visMain$nonHeteroOthersLikeMe == 3)))/length(which(!is.na(visMain$nonHeteroOthersLikeMe))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$nonHeteroOthersLikeMe == 4))`, or `r round(length(which(visMain$nonHeteroOthersLikeMe == 4))/length(which(!is.na(visMain$nonHeteroOthersLikeMe))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$nonHeteroOthersLikeMe == 5))+length(which(visMain$nonHeteroOthersLikeMe == 6))+length(which(visMain$nonHeteroOthersLikeMe == 7))`, or `r round((length(which(visMain$nonHeteroOthersLikeMe == 5))+length(which(visMain$nonHeteroOthersLikeMe == 6))+length(which(visMain$nonHeteroOthersLikeMe == 7)))/length(which(!is.na(visMain$nonHeteroOthersLikeMe))),3)*100`%

##### central tendency

```{r tableOfSexualityStats}
#| label: nonhetero-stats-table
#| tbl-cap: "Statistics for responses to statements regarding sexual orientation"
#| output: asis

visMain |>
  select(nonHeteroNegPerc:nonHeteroOthersLikeMe) |>
  tableLikert(
    lowerBound = "1 = Strongly disagree",
    upperBound = "7 = Strongly agree"
  )
  
```

#### [some remarks]

-   Of the 36 people who indicated that they were associated with non-heterosexuality, only one thought it had affected their interactions with the *PsychoPy*<sup>&reg;</sup> community, and they mostly disagreed with negative treatment by others and disagreed with statements expressing low self-regard. They were neutral-ish on whether they'd like to see others more like them in the community.

---

### race / culture

The third EDI category is *race* and/or *culture*. As before, we present the responses to the issue of identity, followed by a table of descriptions (supplied by some of the participants). This is followed by whether the participant felt affected in the *PsychoPy*<sup>&reg;</sup> community by that identity. Finally, we summarise the participants responses to items listed under *treatment* (by others), *self-regard*, and *isolation*. 

#### identity

##### visualisation

```{r plotRaceCulture}
#| label: raceculture-plot
#| fig-alt: "Barplot of responses to: 'Do you, or might others who know you well, consider you part of a race/culture that is potentially discriminated against?'"

visMain |> 
  select(raceCulture) |> 
  ostFreqPlot(
    ostColour = ostOrange,
    sorting = "none"
  )

```

##### verbal summary

Below, we describe the numbers in the figure above.

- *`r get_label(visMain$raceCulture)`*\
  - Total responses: `r length(which(!is.na(visMain$raceCulture)))` (out of `r nrow(visMain)`)  or `r round(length(which(!is.na(visMain$raceCulture)))/nrow(visMain),3)*100`% of the total\
  - Those who selected ***no***: `r length(which(visMain$raceCulture == 0))`, or `r round(length(which(visMain$raceCulture == 0))/length(which(!is.na(visMain$raceCulture))),3)*100`%\
  - Those who selected ***yes***: `r length(which(visMain$raceCulture == 1))`, or `r round(length(which(visMain$raceCulture == 1))/length(which(!is.na(visMain$raceCulture))),3)*100`%

---

#### descriptions

If participants chose ***yes*** as an answer above, they were given the opportunity to describe their race(s) and/or culture(s), though doing so was optional. For those who did, the table below lists the descriptions they provided.

The question was as follows:

>`r get_label(visMain$raceCultureDesc)`

```{r tableRaceCulturerDesc}
#| label: raceculture-desc-table
#| tbl-cap: Descriptions of race and/or culture volunteered by participants

visMain |> 
  count(raceCultureDesc) |>
  arrange(desc(n)) |>
  datatable(
    class = 'cell-border stripe',
    colnames = c(
      "Feel free to describe your race and/or culture here (or not)",
      "count"
      ),
    
    options = list(
      columnDefs = list(
        list(
          targets = 1,
          render = JS(
            "function(data, type, row, meta) {",
            "return data === null ? 'NA' : data;",
            "}"
            )
          )
        )
      )
    )

```

---

#### felt affected

The sections directly below summarise, both visually and verbally, the answer to the following question:

>`r get_label(visMain$raceCultureAffected)`

##### visualisation

```{r plotRaceCultureAffected}
#| label: raceculture-affected-plot
#| fig-alt: "Frequency barplot of responses to the following statement: 'Do you feel that your race and/or culture has affected your interactions with the PsychoPy community or software ecosystem?' If participants chose to respond, they could respond with either 'yes' or 'no.'"


visMain |> 
  select(raceCultureAffected) |> 
  ostFreqPlot(
    ostColour = ostYellow,
    sorting = "none"
  )

```

##### verbal summary

Below, we describe the numbers in the figure above.

- *`r get_label(visMain$raceCultureAffected)`*\
  - Total responses: `r length(which(!is.na(visMain$raceCultureAffected)))` (out of `r nrow(visMain)`)  or `r round(length(which(!is.na(visMain$raceCultureAffected)))/nrow(visMain),3)*100`% of the total\
  - Those who selected ***no***: `r length(which(visMain$raceCultureAffected == 0))`, or `r round(length(which(visMain$raceCultureAffected == 0))/length(which(!is.na(visMain$raceCultureAffected))),3)*100`% of those who responded to this question.\
  - Those who selected ***yes***: `r length(which(visMain$raceCultureAffected == 1))`, or `r round(length(which(visMain$raceCultureAffected == 1))/length(which(!is.na(visMain$raceCultureAffected))),3)*100`% of those who responded to this question.
  
::: {.callout-important}
##### Important insight
This question regarding *race* and/or *culture* determined whether or not the participant saw the items regarding *treatment (by others)*, *self-regard*, and *isolation*.

The `r numbers_to_words(length(which(visMain$raceCultureAffected==1)))` ***yes*** responses here comprise `r round(length(which(visMain$raceCultureAffected==1))/length(which(visMain$raceCulture==1)),3)*100`% of the `r length(which(visMain$raceCulture==1))` who identified with one or more race(s) and/or culture(s) that were potentially discriminated against. In contrast, the `r length(which(visMain$raceCultureAffected==0))` ***no*** responses here comprise `r round(length(which(visMain$raceCultureAffected==0))/length(which(visMain$raceCulture==1)),3)*100`%
:::

---

#### treatment, self-regard, isolation

The following statements were seen only by the subset of participants noted above. Specifically, they were restricted to the **`r numbers_to_words(length(which(visMain$raceCultureAffected==1)))`** who replied ***yes*** to the question asking them whether they had felt that their racial and/or cultural identity has affected their interactions with the *PsychoPy*<sup>&reg;</sup> community.

The exact questions are listed in the verbal summary after the visualisation.

##### visualisation

```{r plotRaceCultureLikert}
#| warning: false
#| label: raceculture-likert-plot
#| fig-alt: "Stacked frequency barplots of responses to statements on race/culture, categorized into the following: treatment by others, self-regard, and isolation." 

visMain |>
  select(raceCultureNegPerc:raceCultureOthersLikeMe) |> 
  stackedLikertGroups(
    likertTitle = "Race(s) and/or Culture(s)")

```

##### verbal summary

Below, we describe the numbers in the figure above, but in the order in which the items appeared in the survey.

###### treatment by others

- *`r get_label(visMain$raceCultureNegPerc)`*\
  - Total responses: `r length(which(!is.na(visMain$raceCultureNegPerc)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$raceCultureNegPerc)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$raceCultureNegPerc == 1))+length(which(visMain$raceCultureNegPerc == 2))+length(which(visMain$raceCultureNegPerc == 3))`, or `r round((length(which(visMain$raceCultureNegPerc == 1))+length(which(visMain$raceCultureNegPerc == 2))+length(which(visMain$raceCultureNegPerc == 3)))/length(which(!is.na(visMain$raceCultureNegPerc))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$raceCultureNegPerc == 4))`, or `r round(length(which(visMain$raceCultureNegPerc == 4))/length(which(!is.na(visMain$raceCultureNegPerc))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$raceCultureNegPerc == 5))+length(which(visMain$raceCultureNegPerc == 6))+length(which(visMain$raceCultureNegPerc == 7))`, or `r round((length(which(visMain$raceCultureNegPerc == 5))+length(which(visMain$raceCultureNegPerc == 6))+length(which(visMain$raceCultureNegPerc == 7)))/length(which(!is.na(visMain$raceCultureNegPerc))),3)*100`%

- *`r get_label(visMain$raceCultureHideID)`*\
  - Total responses: `r length(which(!is.na(visMain$raceCultureHideID)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$raceCultureHideID)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$raceCultureHideID == 1))+length(which(visMain$raceCultureHideID == 2))+length(which(visMain$raceCultureHideID == 3))`, or `r round((length(which(visMain$raceCultureHideID == 1))+length(which(visMain$raceCultureHideID == 2))+length(which(visMain$raceCultureHideID == 3)))/length(which(!is.na(visMain$raceCultureHideID))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$raceCultureHideID == 4))`, or `r round(length(which(visMain$raceCultureHideID == 4))/length(which(!is.na(visMain$raceCultureHideID))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$raceCultureHideID == 5))+length(which(visMain$raceCultureHideID == 6))+length(which(visMain$raceCultureHideID == 7))`, or `r round((length(which(visMain$raceCultureHideID == 5))+length(which(visMain$raceCultureHideID == 6))+length(which(visMain$raceCultureHideID == 7)))/length(which(!is.na(visMain$raceCultureHideID))),3)*100`%
  
- *`r get_label(visMain$raceCultureIgnored)`*\
  - Total responses: `r length(which(!is.na(visMain$raceCultureIgnored)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$raceCultureIgnored)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$raceCultureIgnored == 1))+length(which(visMain$raceCultureIgnored == 2))+length(which(visMain$raceCultureIgnored == 3))`, or `r round((length(which(visMain$raceCultureIgnored == 1))+length(which(visMain$raceCultureIgnored == 2))+length(which(visMain$raceCultureIgnored == 3)))/length(which(!is.na(visMain$raceCultureIgnored))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$raceCultureIgnored == 4))`, or `r round(length(which(visMain$raceCultureIgnored == 4))/length(which(!is.na(visMain$raceCultureIgnored))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$raceCultureIgnored == 5))+length(which(visMain$raceCultureIgnored == 6))+length(which(visMain$raceCultureIgnored == 7))`, or `r round((length(which(visMain$raceCultureIgnored == 5))+length(which(visMain$raceCultureIgnored == 6))+length(which(visMain$raceCultureIgnored == 7)))/length(which(!is.na(visMain$raceCultureIgnored))),3)*100`%
  
- *`r get_label(visMain$raceCultureDerisive)`*\
  - Total responses: `r length(which(!is.na(visMain$raceCultureDerisive)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$raceCultureDerisive)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$raceCultureDerisive == 1))+length(which(visMain$raceCultureDerisive == 2))+length(which(visMain$raceCultureDerisive == 3))`, or `r round((length(which(visMain$raceCultureDerisive == 1))+length(which(visMain$raceCultureDerisive == 2))+length(which(visMain$raceCultureDerisive == 3)))/length(which(!is.na(visMain$raceCultureDerisive))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$raceCultureDerisive == 4))`, or `r round(length(which(visMain$raceCultureDerisive == 4))/length(which(!is.na(visMain$raceCultureDerisive))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$raceCultureDerisive == 5))+length(which(visMain$raceCultureDerisive == 6))+length(which(visMain$raceCultureDerisive == 7))`, or `r round((length(which(visMain$raceCultureDerisive == 5))+length(which(visMain$raceCultureDerisive == 6))+length(which(visMain$raceCultureDerisive == 7)))/length(which(!is.na(visMain$raceCultureDerisive))),3)*100`%
  
- *`r get_label(visMain$raceCultureMicroaggressions)`*\
  - Total responses: `r length(which(!is.na(visMain$raceCultureMicroaggressions)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$raceCultureMicroaggressions)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$raceCultureMicroaggressions == 1))+length(which(visMain$raceCultureMicroaggressions == 2))+length(which(visMain$raceCultureMicroaggressions == 3))`, or `r round((length(which(visMain$raceCultureMicroaggressions == 1))+length(which(visMain$raceCultureMicroaggressions == 2))+length(which(visMain$raceCultureMicroaggressions == 3)))/length(which(!is.na(visMain$raceCultureMicroaggressions))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$raceCultureMicroaggressions == 4))`, or `r round(length(which(visMain$raceCultureMicroaggressions == 4))/length(which(!is.na(visMain$raceCultureMicroaggressions))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$raceCultureMicroaggressions == 5))+length(which(visMain$raceCultureMicroaggressions == 6))+length(which(visMain$raceCultureMicroaggressions == 7))`, or `r round((length(which(visMain$raceCultureMicroaggressions == 5))+length(which(visMain$raceCultureMicroaggressions == 6))+length(which(visMain$raceCultureMicroaggressions == 7)))/length(which(!is.na(visMain$raceCultureMicroaggressions))),3)*100`%
  
###### self-regard

- *`r get_label(visMain$raceCultureSelfDoubt)`*\
  - Total responses: `r length(which(!is.na(visMain$raceCultureSelfDoubt)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$raceCultureSelfDoubt)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$raceCultureSelfDoubt == 1))+length(which(visMain$raceCultureSelfDoubt == 2))+length(which(visMain$raceCultureSelfDoubt == 3))`, or `r round((length(which(visMain$raceCultureSelfDoubt == 1))+length(which(visMain$raceCultureSelfDoubt == 2))+length(which(visMain$raceCultureSelfDoubt == 3)))/length(which(!is.na(visMain$raceCultureSelfDoubt))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$raceCultureSelfDoubt == 4))`, or `r round(length(which(visMain$raceCultureSelfDoubt == 4))/length(which(!is.na(visMain$raceCultureSelfDoubt))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$raceCultureSelfDoubt == 5))+length(which(visMain$raceCultureSelfDoubt == 6))+length(which(visMain$raceCultureSelfDoubt == 7))`, or `r round((length(which(visMain$raceCultureSelfDoubt == 5))+length(which(visMain$raceCultureSelfDoubt == 6))+length(which(visMain$raceCultureSelfDoubt == 7)))/length(which(!is.na(visMain$raceCultureSelfDoubt))),3)*100`%

- *`r get_label(visMain$raceCultureStereotypeThreat)`*\
  - Total responses: `r length(which(!is.na(visMain$raceCultureStereotypeThreat)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$raceCultureStereotypeThreat)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$raceCultureStereotypeThreat == 1))+length(which(visMain$raceCultureStereotypeThreat == 2))+length(which(visMain$raceCultureStereotypeThreat == 3))`, or `r round((length(which(visMain$raceCultureStereotypeThreat == 1))+length(which(visMain$raceCultureStereotypeThreat == 2))+length(which(visMain$raceCultureStereotypeThreat == 3)))/length(which(!is.na(visMain$raceCultureStereotypeThreat))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$raceCultureStereotypeThreat == 4))`, or `r round(length(which(visMain$raceCultureStereotypeThreat == 4))/length(which(!is.na(visMain$raceCultureStereotypeThreat))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$raceCultureStereotypeThreat == 5))+length(which(visMain$raceCultureStereotypeThreat == 6))+length(which(visMain$raceCultureStereotypeThreat == 7))`, or `r round((length(which(visMain$raceCultureStereotypeThreat == 5))+length(which(visMain$raceCultureStereotypeThreat == 6))+length(which(visMain$raceCultureStereotypeThreat == 7)))/length(which(!is.na(visMain$raceCultureStereotypeThreat))),3)*100`%
  
###### isolation
  
- *`r get_label(visMain$raceCultureOthersLikeMe)`*\
  - Total responses: `r length(which(!is.na(visMain$raceCultureOthersLikeMe)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$raceCultureOthersLikeMe)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$raceCultureOthersLikeMe == 1))+length(which(visMain$raceCultureOthersLikeMe == 2))+length(which(visMain$raceCultureOthersLikeMe == 3))`, or `r round((length(which(visMain$raceCultureOthersLikeMe == 1))+length(which(visMain$raceCultureOthersLikeMe == 2))+length(which(visMain$raceCultureOthersLikeMe == 3)))/length(which(!is.na(visMain$raceCultureOthersLikeMe))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$raceCultureOthersLikeMe == 4))`, or `r round(length(which(visMain$raceCultureOthersLikeMe == 4))/length(which(!is.na(visMain$raceCultureOthersLikeMe))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$raceCultureOthersLikeMe == 5))+length(which(visMain$raceCultureOthersLikeMe == 6))+length(which(visMain$raceCultureOthersLikeMe == 7))`, or `r round((length(which(visMain$raceCultureOthersLikeMe == 5))+length(which(visMain$raceCultureOthersLikeMe == 6))+length(which(visMain$raceCultureOthersLikeMe == 7)))/length(which(!is.na(visMain$raceCultureOthersLikeMe))),3)*100`%

##### central tendency

```{r tableOfRacecultureStats}
#| label: raceculture-stats-table
#| tbl-cap: "Statistics for responses to statements regarding race and/or culture"
#| output: asis

visMain |>
  select(raceCultureNegPerc:raceCultureOthersLikeMe) |> 
  tableLikert(
    lowerBound = "1 = Strongly disagree",
    upperBound = "7 = Strongly agree"
  )

```

#### [some remarks]

- Out of the 42 people who indicated that they were of a race and/or culture that is potentially discriminated against, only 3 indicated that they had felt that their interactions within the *PsychoPy*<sup>&reg;</sup> community had been affected because of it. That seems fairly low (though still a problem).\
- Those three seemed evenly split on most of the *treatment* category (with the exception of intentionally derisive comments, where there was strictly disagreement). And all of them expressed some sort of agreement with the *self-regard* and *isolation* items.

---

### disability / neurodivergence

The fourth EDI category is *disability* and/or *neurodivergence*. As above, we present the responses to the issue of identity, followed by a table of descriptions (supplied by some of the participants). This is followed by whether the participant felt affected in the *PsychoPy*<sup>&reg;</sup> community by that identity. Finally, we summarise the participants responses to items listed under *treatment* (by others), *self-regard*, and *isolation*.

#### identity

##### visualisation

```{r plotDisability}
#| label: disability-plot
#| fig-alt: "Frequency barplot of responses to the following question: 'Do you, or might others who know you well, consider you disabled and/or neurodivergent (i.e., visible or invisible; e.g., blind, paralysed, cerebral palsy, ASD, ADHD)?' If participants chose to respond, they could respond with either 'yes' or 'no.'"

visMain |> 
  select(disability) |> 
  ostFreqPlot(
    ostColour = ostBlue,
    sorting = "none"
  )

```

##### verbal summary

Below, we describe the numbers in the figure above.

- *`r get_label(visMain$disability)`*\
  - Total responses: `r length(which(!is.na(visMain$disability)))` (out of `r nrow(visMain)`)  or `r round(length(which(!is.na(visMain$disability)))/nrow(visMain),3)*100`% of the total\
  - Those who selected ***no***: `r length(which(visMain$disability == 0))`, or `r round(length(which(visMain$disability == 0))/length(which(!is.na(visMain$disability))),3)*100`%\
  - Those who selected ***yes***: `r length(which(visMain$disability == 1))`, or `r round(length(which(visMain$disability == 1))/length(which(!is.na(visMain$disability))),3)*100`%

---

#### descriptions

If participants chose ***yes*** as an answer above, they were given the opportunity to describe their disability(-ies) and/or neurodivergence, though doing so was optional. For those who did, the table below lists the descriptions they provided.

The question was as follows:

>`r get_label(visMain$disabilityDesc)`


```{r tableDisabilityDesc}
#| label: disability-desc-table
#| tbl-cap: Descriptions of disability volunteered by participants

visMain |> 
  count(disabilityDesc) |>
  arrange(desc(n)) |>
  datatable(
    class = 'cell-border stripe',
    colnames = c(
      "Feel free to describe your disabled and/or neurodivergent status (or not)",
      "count"
      ),
    
    options = list(
      columnDefs = list(
        list(
          targets = 1,
          render = JS(
            "function(data, type, row, meta) {",
            "return data === null ? 'NA' : data;",
            "}"
            )
          )
        )
      )
    )

```

---

#### felt affected

The sections directly below summarise, both visually and verbally, the answer to the following question:

>`r get_label(visMain$disabilityAffected)`

##### visualisation

```{r plotDisabilityAffected}
#| label: disability-affected-plot
#| fig-alt: "Frequency barplot of responses to the following statement: 'Do you feel that your disabled and/or neurodivergent status has affected your interactions with the PsychoPy community or software ecosystem?' If participants chose to respond, they could respond with either 'yes' or 'no.'"

visMain |> 
  select(disabilityAffected) |> 
  ostFreqPlot(
    ostColour = ostOrange,
    sorting = "none"
  )

```

##### verbal summary

Below, we describe the numbers in the figure above.

- *`r get_label(visMain$disabilityAffected)`*\
  - Total responses: `r length(which(!is.na(visMain$disabilityAffected)))` (out of `r nrow(visMain)`)  or `r round(length(which(!is.na(visMain$disabilityAffected)))/nrow(visMain),3)*100`% of the total\
  - Those who selected ***no***: `r length(which(visMain$disabilityAffected == 0))`, or `r round(length(which(visMain$disabilityAffected == 0))/length(which(!is.na(visMain$disabilityAffected))),3)*100`% of those who responded to this question.\
  - Those who selected ***yes***: `r length(which(visMain$disabilityAffected == 1))`, or `r round(length(which(visMain$disabilityAffected == 1))/length(which(!is.na(visMain$disabilityAffected))),3)*100`% of those who responded to this question.
  
::: {.callout-important}
##### Important insight
This question regarding *disability* and/or *neurodivergence* determined whether or not the participant saw the items regarding *treatment (by others)*, *self-regard*, and *isolation*.

The `r numbers_to_words(length(which(visMain$disabilityAffected==1)))` ***yes*** responses here comprise `r round(length(which(visMain$disabilityAffected==1))/length(which(visMain$disability==1)),3)*100`% of the `r length(which(visMain$disability==1))` who identified with disability or neurodivergence. In contrast, the `r length(which(visMain$disabilityAffected==0))` ***no*** responses here comprise `r round(length(which(visMain$disabilityAffected==0))/length(which(visMain$disability==1)),3)*100`%
:::

---

#### treatment, self-regard, isolation

The following statements were seen only by the subset of participants noted above. Specifically, they were restricted to the **`r numbers_to_words(length(which(visMain$disabilityAffected==1)))`** who replied ***yes*** to the question asking them whether they had felt that their disability and/or neurodivergence has affected their interactions with the *PsychoPy*<sup>&reg;</sup> community.

The exact questions are listed in the verbal summary after the visualisation.

##### visualisation

```{r plotDisabilityLikert}
#| warning: false
#| label: disability-likert-plot
#| fig-alt: "Stacked frequency barplots of responses to disability/neurodivergence, categorized into the following: treatment by others, self-regard, and isolation." 

visMain |>
  select(disabilityNegPerc:disabilityOthersLikeMe) |> 
  stackedLikertGroups(likertTitle = "Disability and/or neurodivergence")

```

##### verbal summary

Below, we describe the numbers in the figure above, but in the order in which the items appeared in the survey.

###### treatment by others

- *`r get_label(visMain$disabilityNegPerc)`*\
  - Total responses: `r length(which(!is.na(visMain$disabilityNegPerc)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$disabilityNegPerc)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$disabilityNegPerc == 1))+length(which(visMain$disabilityNegPerc == 2))+length(which(visMain$disabilityNegPerc == 3))`, or `r round((length(which(visMain$disabilityNegPerc == 1))+length(which(visMain$disabilityNegPerc == 2))+length(which(visMain$disabilityNegPerc == 3)))/length(which(!is.na(visMain$disabilityNegPerc))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$disabilityNegPerc == 4))`, or `r round(length(which(visMain$disabilityNegPerc == 4))/length(which(!is.na(visMain$disabilityNegPerc))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$disabilityNegPerc == 5))+length(which(visMain$disabilityNegPerc == 6))+length(which(visMain$disabilityNegPerc == 7))`, or `r round((length(which(visMain$disabilityNegPerc == 5))+length(which(visMain$disabilityNegPerc == 6))+length(which(visMain$disabilityNegPerc == 7)))/length(which(!is.na(visMain$disabilityNegPerc))),3)*100`%

- *`r get_label(visMain$disabilityHideID)`*\
  - Total responses: `r length(which(!is.na(visMain$disabilityHideID)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$disabilityHideID)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$disabilityHideID == 1))+length(which(visMain$disabilityHideID == 2))+length(which(visMain$disabilityHideID == 3))`, or `r round((length(which(visMain$disabilityHideID == 1))+length(which(visMain$disabilityHideID == 2))+length(which(visMain$disabilityHideID == 3)))/length(which(!is.na(visMain$disabilityHideID))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$disabilityHideID == 4))`, or `r round(length(which(visMain$disabilityHideID == 4))/length(which(!is.na(visMain$disabilityHideID))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$disabilityHideID == 5))+length(which(visMain$disabilityHideID == 6))+length(which(visMain$disabilityHideID == 7))`, or `r round((length(which(visMain$disabilityHideID == 5))+length(which(visMain$disabilityHideID == 6))+length(which(visMain$disabilityHideID == 7)))/length(which(!is.na(visMain$disabilityHideID))),3)*100`%
  
- *`r get_label(visMain$disabilityIgnored)`*\
  - Total responses: `r length(which(!is.na(visMain$disabilityIgnored)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$disabilityIgnored)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$disabilityIgnored == 1))+length(which(visMain$disabilityIgnored == 2))+length(which(visMain$disabilityIgnored == 3))`, or `r round((length(which(visMain$disabilityIgnored == 1))+length(which(visMain$disabilityIgnored == 2))+length(which(visMain$disabilityIgnored == 3)))/length(which(!is.na(visMain$disabilityIgnored))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$disabilityIgnored == 4))`, or `r round(length(which(visMain$disabilityIgnored == 4))/length(which(!is.na(visMain$disabilityIgnored))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$disabilityIgnored == 5))+length(which(visMain$disabilityIgnored == 6))+length(which(visMain$disabilityIgnored == 7))`, or `r round((length(which(visMain$disabilityIgnored == 5))+length(which(visMain$disabilityIgnored == 6))+length(which(visMain$disabilityIgnored == 7)))/length(which(!is.na(visMain$disabilityIgnored))),3)*100`%
  
- *`r get_label(visMain$disabilityDerisive)`*\
  - Total responses: `r length(which(!is.na(visMain$disabilityDerisive)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$disabilityDerisive)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$disabilityDerisive == 1))+length(which(visMain$disabilityDerisive == 2))+length(which(visMain$disabilityDerisive == 3))`, or `r round((length(which(visMain$disabilityDerisive == 1))+length(which(visMain$disabilityDerisive == 2))+length(which(visMain$disabilityDerisive == 3)))/length(which(!is.na(visMain$disabilityDerisive))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$disabilityDerisive == 4))`, or `r round(length(which(visMain$disabilityDerisive == 4))/length(which(!is.na(visMain$disabilityDerisive))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$disabilityDerisive == 5))+length(which(visMain$disabilityDerisive == 6))+length(which(visMain$disabilityDerisive == 7))`, or `r round((length(which(visMain$disabilityDerisive == 5))+length(which(visMain$disabilityDerisive == 6))+length(which(visMain$disabilityDerisive == 7)))/length(which(!is.na(visMain$disabilityDerisive))),3)*100`%
  
- *`r get_label(visMain$disabilityMicroaggressions)`*\
  - Total responses: `r length(which(!is.na(visMain$disabilityMicroaggressions)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$disabilityMicroaggressions)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$disabilityMicroaggressions == 1))+length(which(visMain$disabilityMicroaggressions == 2))+length(which(visMain$disabilityMicroaggressions == 3))`, or `r round((length(which(visMain$disabilityMicroaggressions == 1))+length(which(visMain$disabilityMicroaggressions == 2))+length(which(visMain$disabilityMicroaggressions == 3)))/length(which(!is.na(visMain$disabilityMicroaggressions))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$disabilityMicroaggressions == 4))`, or `r round(length(which(visMain$disabilityMicroaggressions == 4))/length(which(!is.na(visMain$disabilityMicroaggressions))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$disabilityMicroaggressions == 5))+length(which(visMain$disabilityMicroaggressions == 6))+length(which(visMain$disabilityMicroaggressions == 7))`, or `r round((length(which(visMain$disabilityMicroaggressions == 5))+length(which(visMain$disabilityMicroaggressions == 6))+length(which(visMain$disabilityMicroaggressions == 7)))/length(which(!is.na(visMain$disabilityMicroaggressions))),3)*100`%
  
###### self-regard

- *`r get_label(visMain$disabilitySelfDoubt)`*\
  - Total responses: `r length(which(!is.na(visMain$disabilitySelfDoubt)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$disabilitySelfDoubt)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$disabilitySelfDoubt == 1))+length(which(visMain$disabilitySelfDoubt == 2))+length(which(visMain$disabilitySelfDoubt == 3))`, or `r round((length(which(visMain$disabilitySelfDoubt == 1))+length(which(visMain$disabilitySelfDoubt == 2))+length(which(visMain$disabilitySelfDoubt == 3)))/length(which(!is.na(visMain$disabilitySelfDoubt))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$disabilitySelfDoubt == 4))`, or `r round(length(which(visMain$disabilitySelfDoubt == 4))/length(which(!is.na(visMain$disabilitySelfDoubt))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$disabilitySelfDoubt == 5))+length(which(visMain$disabilitySelfDoubt == 6))+length(which(visMain$disabilitySelfDoubt == 7))`, or `r round((length(which(visMain$disabilitySelfDoubt == 5))+length(which(visMain$disabilitySelfDoubt == 6))+length(which(visMain$disabilitySelfDoubt == 7)))/length(which(!is.na(visMain$disabilitySelfDoubt))),3)*100`%

- *`r get_label(visMain$disabilityStereotypeThreat)`*\
  - Total responses: `r length(which(!is.na(visMain$disabilityStereotypeThreat)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$disabilityStereotypeThreat)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$disabilityStereotypeThreat == 1))+length(which(visMain$disabilityStereotypeThreat == 2))+length(which(visMain$disabilityStereotypeThreat == 3))`, or `r round((length(which(visMain$disabilityStereotypeThreat == 1))+length(which(visMain$disabilityStereotypeThreat == 2))+length(which(visMain$disabilityStereotypeThreat == 3)))/length(which(!is.na(visMain$disabilityStereotypeThreat))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$disabilityStereotypeThreat == 4))`, or `r round(length(which(visMain$disabilityStereotypeThreat == 4))/length(which(!is.na(visMain$disabilityStereotypeThreat))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$disabilityStereotypeThreat == 5))+length(which(visMain$disabilityStereotypeThreat == 6))+length(which(visMain$disabilityStereotypeThreat == 7))`, or `r round((length(which(visMain$disabilityStereotypeThreat == 5))+length(which(visMain$disabilityStereotypeThreat == 6))+length(which(visMain$disabilityStereotypeThreat == 7)))/length(which(!is.na(visMain$disabilityStereotypeThreat))),3)*100`%
  
###### isolation
  
- *`r get_label(visMain$disabilityOthersLikeMe)`*\
  - Total responses: `r length(which(!is.na(visMain$disabilityOthersLikeMe)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$disabilityOthersLikeMe)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$disabilityOthersLikeMe == 1))+length(which(visMain$disabilityOthersLikeMe == 2))+length(which(visMain$disabilityOthersLikeMe == 3))`, or `r round((length(which(visMain$disabilityOthersLikeMe == 1))+length(which(visMain$disabilityOthersLikeMe == 2))+length(which(visMain$disabilityOthersLikeMe == 3)))/length(which(!is.na(visMain$disabilityOthersLikeMe))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$disabilityOthersLikeMe == 4))`, or `r round(length(which(visMain$disabilityOthersLikeMe == 4))/length(which(!is.na(visMain$disabilityOthersLikeMe))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$disabilityOthersLikeMe == 5))+length(which(visMain$disabilityOthersLikeMe == 6))+length(which(visMain$disabilityOthersLikeMe == 7))`, or `r round((length(which(visMain$disabilityOthersLikeMe == 5))+length(which(visMain$disabilityOthersLikeMe == 6))+length(which(visMain$disabilityOthersLikeMe == 7)))/length(which(!is.na(visMain$disabilityOthersLikeMe))),3)*100`%

##### central tendency

```{r tableOfDisabilityStats}
#| label: disability-stats-table
#| tbl-cap: "Statistics for responses to statements regarding disability"
#| output: asis

visMain |>
  select(disabilityNegPerc:disabilityOthersLikeMe) |> 
  tableLikert(
    lowerBound = "1 = Strongly disagree",
    upperBound = "7 = Strongly agree"
  )

```

#### [some remarks]

- Of the 28 participants who indicated some sort of disability and/or neurodivergence, six indicated that they thought that status had affected their interactions in the *PsychoPy*<sup>&reg;</sup> community. I think this is the highest percentage of all the groups.\
- Interestingly, among those six, there was fairly widespread disagreement with the notion that they had been treated poorly by others. Rather, there is much more agreement with the self-regard issues. That is, 4-5 of those six seem to indicate lack of confidence.\
- A slight majority of them also feel isolated.

---

### written language dominance

The fifth EDI category is *written language dominance*. As before, we present the responses to the issue of identity, followed by a table of descriptions (supplied by some of the participants). This is followed by whether the participant felt affected in the *PsychoPy*<sup>&reg;</sup> community by that identity. Finally, we summarise the participants responses to items listed under *treatment* (by others), *self-regard*, and *isolation*.

#### identity

##### visualisation

```{r plotDomLang}
#| label: dominant-language-plot
#| fig-alt: "Frequency barplot of responses to the following question: 'Is your dominant (preferred) written language English?' If participants chose to respond, they could respond with either 'yes' or 'no.'"

visMain |> 
  select(domLangEnglish) |> 
  ostFreqPlot(
    ostColour = ostYellow,
    sorting = "none"
  )

```

##### verbal summary

- *`r get_label(visMain$domLangEnglish)`*\
  - Total responses: `r length(which(!is.na(visMain$domLangEnglish)))` (out of `r nrow(visMain)`)  or `r round(length(which(!is.na(visMain$domLangEnglish)))/nrow(visMain),3)*100`% of the total\
  - Those who selected ***no***: `r length(which(visMain$domLangEnglish == 0))`, or `r round(length(which(visMain$domLangEnglish == 0))/length(which(!is.na(visMain$domLangEnglish))),3)*100`%\
  - Those who selected ***yes***: `r length(which(visMain$domLangEnglish == 1))`, or `r round(length(which(visMain$domLangEnglish == 1))/length(which(!is.na(visMain$domLangEnglish))),3)*100`%

---

#### descriptions

If participants chose ***no*** as an answer above, they were given the opportunity to describe their dominant language, though doing so was optional. For those who did, the table below lists the descriptions they provided.

The question was as follows:

>`r get_label(visMain$domLangDesc)`

```{r tableDomLangDesc}
#| label: domlang-desc-table
#| tbl-cap: Non-dominant languages volunteered by participants

visMain |> 
  count(domLangDesc) |>
  arrange(desc(n)) |>
  datatable(
    class = 'cell-border stripe',
    colnames = c(
      "Feel free to type in your dominant language (or not)",
      "count"
      ),
    
    options = list(
      columnDefs = list(
        list(
          targets = 1,
          render = JS(
            "function(data, type, row, meta) {",
            "return data === null ? 'NA' : data;",
            "}"
            )
          )
        )
      )
    )

```

---

#### felt affected

The sections directly below summarise, both visually and verbally, the answer to the following question:

>`r get_label(visMain$domLangAffected)`

##### visualisation

```{r plotDomLangAffected}
#| label: dominant-language-affected-plot
#| fig-alt: "Frequency barplot of responses to the following statement: 'Do you feel that your dominant language has affected your interactions with the PsychoPy community or software ecosystem?' If participants chose to respond, they could respond with either 'yes' or 'no.'"

visMain |> 
  select(domLangAffected) |> 
  ostFreqPlot(
    ostColour = ostBlue,
    sorting = "none"
  )

```

##### verbal summary

Below, we describe the numbers in the figure above.

- *`r get_label(visMain$domLangAffected)`*\
  - Total responses: `r length(which(!is.na(visMain$domLangAffected)))` (out of `r nrow(visMain)`)  or `r round(length(which(!is.na(visMain$domLangAffected)))/nrow(visMain),3)*100`% of the total\
  - Those who selected ***no***: `r length(which(visMain$domLangAffected == 0))`, or `r round(length(which(visMain$domLangAffected == 0))/length(which(!is.na(visMain$domLangAffected))),3)*100`% of those who responded to this question.\
  - Those who selected ***yes***: `r length(which(visMain$domLangAffected == 1))`, or `r round(length(which(visMain$domLangAffected == 1))/length(which(!is.na(visMain$domLangAffected))),3)*100`% of those who responded to this question.

::: {.callout-important}
##### Important insight
This question regarding *language dominance* determined whether or not the participant saw the items regarding *treatment (by others)*, *self-regard*, and *isolation*.

The `r numbers_to_words(length(which(visMain$domLangAffected==1)))` ***yes*** responses here comprise `r round(length(which(visMain$domLangAffected==1))/length(which(visMain$domLangEnglish==0)),3)*100`% of the `r length(which(visMain$domLangEnglish==0))` who identified as having a dominant written language other than English. In contrast, the `r length(which(visMain$domLangAffected==0))` ***no*** responses here comprise `r round(length(which(visMain$domLangAffected==0))/length(which(visMain$domLangEnglish==0)),3)*100`%
:::

---

#### treatment, self-regard, isolation

The following statements were seen only by the subset of participants noted above. Specifically, they were restricted to the **`r numbers_to_words(length(which(visMain$domLangAffected==1)))`** who replied ***yes*** to the question asking them whether they had felt that their language dominance has affected their interactions with the *PsychoPy*<sup>&reg;</sup> community.

The exact questions are listed in the verbal summary after the visualisation.

##### visualisation

```{r plotDomLangLikert}
#| warning: false
#| label: domlang-likert-plot
#| fig-alt: "Stacked frequency barplots of responses to language dominance, categorized by the following: treatment by others, self-regard, and isolation." 

visMain |>
  select(domLangNegPerc:domLangOthersLikeMe) |> 
  stackedLikertGroups(
    likertTitle = "Dominant Language")

```

##### verbal summary

Below, we describe the numbers in the figure above, but in the order in which the items appeared in the survey.

###### treatment by others

- *`r get_label(visMain$domLangNegPerc)`*\
  - Total responses: `r length(which(!is.na(visMain$domLangNegPerc)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$domLangNegPerc)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$domLangNegPerc == 1))+length(which(visMain$domLangNegPerc == 2))+length(which(visMain$domLangNegPerc == 3))`, or `r round((length(which(visMain$domLangNegPerc == 1))+length(which(visMain$domLangNegPerc == 2))+length(which(visMain$domLangNegPerc == 3)))/length(which(!is.na(visMain$domLangNegPerc))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$domLangNegPerc == 4))`, or `r round(length(which(visMain$domLangNegPerc == 4))/length(which(!is.na(visMain$domLangNegPerc))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$domLangNegPerc == 5))+length(which(visMain$domLangNegPerc == 6))+length(which(visMain$domLangNegPerc == 7))`, or `r round((length(which(visMain$domLangNegPerc == 5))+length(which(visMain$domLangNegPerc == 6))+length(which(visMain$domLangNegPerc == 7)))/length(which(!is.na(visMain$domLangNegPerc))),3)*100`%

- *`r get_label(visMain$domLangHideID)`*\
  - Total responses: `r length(which(!is.na(visMain$domLangHideID)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$domLangHideID)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$domLangHideID == 1))+length(which(visMain$domLangHideID == 2))+length(which(visMain$domLangHideID == 3))`, or `r round((length(which(visMain$domLangHideID == 1))+length(which(visMain$domLangHideID == 2))+length(which(visMain$domLangHideID == 3)))/length(which(!is.na(visMain$domLangHideID))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$domLangHideID == 4))`, or `r round(length(which(visMain$domLangHideID == 4))/length(which(!is.na(visMain$domLangHideID))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$domLangHideID == 5))+length(which(visMain$domLangHideID == 6))+length(which(visMain$domLangHideID == 7))`, or `r round((length(which(visMain$domLangHideID == 5))+length(which(visMain$domLangHideID == 6))+length(which(visMain$domLangHideID == 7)))/length(which(!is.na(visMain$domLangHideID))),3)*100`%
  
- *`r get_label(visMain$domLangIgnored)`*\
  - Total responses: `r length(which(!is.na(visMain$domLangIgnored)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$domLangIgnored)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$domLangIgnored == 1))+length(which(visMain$domLangIgnored == 2))+length(which(visMain$domLangIgnored == 3))`, or `r round((length(which(visMain$domLangIgnored == 1))+length(which(visMain$domLangIgnored == 2))+length(which(visMain$domLangIgnored == 3)))/length(which(!is.na(visMain$domLangIgnored))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$domLangIgnored == 4))`, or `r round(length(which(visMain$domLangIgnored == 4))/length(which(!is.na(visMain$domLangIgnored))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$domLangIgnored == 5))+length(which(visMain$domLangIgnored == 6))+length(which(visMain$domLangIgnored == 7))`, or `r round((length(which(visMain$domLangIgnored == 5))+length(which(visMain$domLangIgnored == 6))+length(which(visMain$domLangIgnored == 7)))/length(which(!is.na(visMain$domLangIgnored))),3)*100`%
  
- *`r get_label(visMain$domLangDerisive)`*\
  - Total responses: `r length(which(!is.na(visMain$domLangDerisive)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$domLangDerisive)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$domLangDerisive == 1))+length(which(visMain$domLangDerisive == 2))+length(which(visMain$domLangDerisive == 3))`, or `r round((length(which(visMain$domLangDerisive == 1))+length(which(visMain$domLangDerisive == 2))+length(which(visMain$domLangDerisive == 3)))/length(which(!is.na(visMain$domLangDerisive))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$domLangDerisive == 4))`, or `r round(length(which(visMain$domLangDerisive == 4))/length(which(!is.na(visMain$domLangDerisive))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$domLangDerisive == 5))+length(which(visMain$domLangDerisive == 6))+length(which(visMain$domLangDerisive == 7))`, or `r round((length(which(visMain$domLangDerisive == 5))+length(which(visMain$domLangDerisive == 6))+length(which(visMain$domLangDerisive == 7)))/length(which(!is.na(visMain$domLangDerisive))),3)*100`%
  
- *`r get_label(visMain$domLangMicroaggressions)`*\
  - Total responses: `r length(which(!is.na(visMain$domLangMicroaggressions)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$domLangMicroaggressions)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$domLangMicroaggressions == 1))+length(which(visMain$domLangMicroaggressions == 2))+length(which(visMain$domLangMicroaggressions == 3))`, or `r round((length(which(visMain$domLangMicroaggressions == 1))+length(which(visMain$domLangMicroaggressions == 2))+length(which(visMain$domLangMicroaggressions == 3)))/length(which(!is.na(visMain$domLangMicroaggressions))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$domLangMicroaggressions == 4))`, or `r round(length(which(visMain$domLangMicroaggressions == 4))/length(which(!is.na(visMain$domLangMicroaggressions))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$domLangMicroaggressions == 5))+length(which(visMain$domLangMicroaggressions == 6))+length(which(visMain$domLangMicroaggressions == 7))`, or `r round((length(which(visMain$domLangMicroaggressions == 5))+length(which(visMain$domLangMicroaggressions == 6))+length(which(visMain$domLangMicroaggressions == 7)))/length(which(!is.na(visMain$domLangMicroaggressions))),3)*100`%
  
###### self-regard

- *`r get_label(visMain$domLangSelfDoubt)`*\
  - Total responses: `r length(which(!is.na(visMain$domLangSelfDoubt)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$domLangSelfDoubt)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$domLangSelfDoubt == 1))+length(which(visMain$domLangSelfDoubt == 2))+length(which(visMain$domLangSelfDoubt == 3))`, or `r round((length(which(visMain$domLangSelfDoubt == 1))+length(which(visMain$domLangSelfDoubt == 2))+length(which(visMain$domLangSelfDoubt == 3)))/length(which(!is.na(visMain$domLangSelfDoubt))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$domLangSelfDoubt == 4))`, or `r round(length(which(visMain$domLangSelfDoubt == 4))/length(which(!is.na(visMain$domLangSelfDoubt))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$domLangSelfDoubt == 5))+length(which(visMain$domLangSelfDoubt == 6))+length(which(visMain$domLangSelfDoubt == 7))`, or `r round((length(which(visMain$domLangSelfDoubt == 5))+length(which(visMain$domLangSelfDoubt == 6))+length(which(visMain$domLangSelfDoubt == 7)))/length(which(!is.na(visMain$domLangSelfDoubt))),3)*100`%

- *`r get_label(visMain$domLangStereotypeThreat)`*\
  - Total responses: `r length(which(!is.na(visMain$domLangStereotypeThreat)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$domLangStereotypeThreat)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$domLangStereotypeThreat == 1))+length(which(visMain$domLangStereotypeThreat == 2))+length(which(visMain$domLangStereotypeThreat == 3))`, or `r round((length(which(visMain$domLangStereotypeThreat == 1))+length(which(visMain$domLangStereotypeThreat == 2))+length(which(visMain$domLangStereotypeThreat == 3)))/length(which(!is.na(visMain$domLangStereotypeThreat))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$domLangStereotypeThreat == 4))`, or `r round(length(which(visMain$domLangStereotypeThreat == 4))/length(which(!is.na(visMain$domLangStereotypeThreat))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$domLangStereotypeThreat == 5))+length(which(visMain$domLangStereotypeThreat == 6))+length(which(visMain$domLangStereotypeThreat == 7))`, or `r round((length(which(visMain$domLangStereotypeThreat == 5))+length(which(visMain$domLangStereotypeThreat == 6))+length(which(visMain$domLangStereotypeThreat == 7)))/length(which(!is.na(visMain$domLangStereotypeThreat))),3)*100`%
  
###### isolation
  
- *`r get_label(visMain$domLangOthersLikeMe)`*\
  - Total responses: `r length(which(!is.na(visMain$domLangOthersLikeMe)))` (out of `r nrow(visMain)`) or `r round(length(which(!is.na(visMain$domLangOthersLikeMe)))/nrow(visMain),3)*100`% of the total\
  - Generally ***disagreed***: `r length(which(visMain$domLangOthersLikeMe == 1))+length(which(visMain$domLangOthersLikeMe == 2))+length(which(visMain$domLangOthersLikeMe == 3))`, or `r round((length(which(visMain$domLangOthersLikeMe == 1))+length(which(visMain$domLangOthersLikeMe == 2))+length(which(visMain$domLangOthersLikeMe == 3)))/length(which(!is.na(visMain$domLangOthersLikeMe))),3)*100`%\
  - ***Neutral***: `r length(which(visMain$domLangOthersLikeMe == 4))`, or `r round(length(which(visMain$domLangOthersLikeMe == 4))/length(which(!is.na(visMain$domLangOthersLikeMe))),3)*100`%\
  - Generally ***agreed***: `r length(which(visMain$domLangOthersLikeMe == 5))+length(which(visMain$domLangOthersLikeMe == 6))+length(which(visMain$domLangOthersLikeMe == 7))`, or `r round((length(which(visMain$domLangOthersLikeMe == 5))+length(which(visMain$domLangOthersLikeMe == 6))+length(which(visMain$domLangOthersLikeMe == 7)))/length(which(!is.na(visMain$domLangOthersLikeMe))),3)*100`%

##### central tendency

```{r tableOfDomLangStats}
#| label: domlang-stats-table
#| tbl-cap: "Statistics for responses to statements regarding dominant language"
#| output: asis

visMain |>
  select(domLangNegPerc:domLangOthersLikeMe) |> 
  tableLikert(
    lowerBound = "1 = Strongly disagree",
    upperBound = "7 = Strongly agree"
  )

```

#### [some remarks]

- the percentage of participants dominant in a written language other than English was second only to those indicating one or more disabilities and/or neurodivergence.\
- their dominant concern seems to be isolation rather than treatment by others or self-regard\
- a sizeable minority of them, however, is concerned that they feel they need to hide their language dominance in order to be taken seriously.


---

## background

The first few items on the survey collected information about  general background demographics, including participants' career status, the role they typically play in their usage of *PsychoPy*<sup>&reg;</sup>. 

Unlike the items above that directly address dimensions of equity, diversity, and inclusion, everyone was able to answer the questions below. However, we can still view each item with respect to whether responses varied according to the various groups that respondents identified with.

These are covered in the subsections below.

### career status

This section summarises, both visually and verbally, the answer to the following question:

>`r get_label(visMain$careerStatus)`

Participants had to choose from one of the following:

- *Researcher - early career (e.g. PhD, postdoc)*\
- *Researcher - mid career (e.g. Assistant/Associate Professor)*\
- *Researcher - senior (e.g. Full Professor)*\
- *Technical - junior*\
- *Technical - senior*

#### everyone 

The visualisation below presents responses in descending order of frequency.

```{r plotCareerStatus}
#| label: career-status-plot
#| fig-alt: "Descending frequency barplot of the responses to the following question: 'Roughly speaking, what is your career status?'"

visMain |>
  select(careerStatus) |>
  ostFreqPlot(
    ostColour = ostBlue, 
    sorting = "desc"
    )

```

##### verbal summary 

The verbal summaries below proceed in the order in which the responses appeared in the original survey (i.e., not descending order of response frequency, as in the visualisation above).

With respect to the `r length(which(!is.na(visMain$careerStatus)))` participants who provided an answer to the question regarding their career status, the number of people in each career type are as follows:

- research career\
  - early phase: `r length(which(visMain$careerStatus == "Researcher - early career"))`, or `r round(length(which(visMain$careerStatus == "Researcher - early career"))/length(which(!is.na(visMain$careerStatus))),3)*100`%\
  - middle phase: `r length(which(visMain$careerStatus == "Researcher - mid career"))`, or `r round(length(which(visMain$careerStatus == "Researcher - mid career"))/length(which(!is.na(visMain$careerStatus))),3)*100`%\
  - senior phase: `r length(which(visMain$careerStatus == "Researcher - senior"))`, or `r round(length(which(visMain$careerStatus == "Researcher - senior"))/length(which(!is.na(visMain$careerStatus))),3)*100`%\

- technical career\
  - junior phase: `r length(which(visMain$careerStatus == "Technical - junior"))`, or `r round(length(which(visMain$careerStatus == "Technical - junior"))/length(which(!is.na(visMain$careerStatus))),3)*100`%\
  - senior phase: `r length(which(visMain$careerStatus == "Technical - senior"))`, or `r round(length(which(visMain$careerStatus == "Technical - senior"))/length(which(!is.na(visMain$careerStatus))),3)*100`%

##### [some remarks]

- Looks like almost half of the responses came from early-career researchers

---

#### interactions

##### gender

```{r careerStatusByGender}
#| label: career-status-by-gender-plot
#| fig-alt: "Descending frequency barplot of the responses by gender to the following question: 'Roughly speaking, what is your career status?'"

contingencyPlot(
  df = visMain,
  contingX = "careerStatus",
  contingGrp = "gender",
  colours = ostColours3
  )

```

---

##### sexuality

```{r careerStatusBySexuality}
#| label: career-status-by-sexuality-plot
#| fig-alt: "Descending frequency barplot of the responses by sexual orientation to the following question: 'Roughly speaking, what is your career status?'"

contingencyPlot(
  df = visMain,
  contingX = "careerStatus",
  contingGrp = "nonHeteroCommunity",
  colours = ostColours2rev
  )

```

---

##### race and/or culture

```{r careerStatusByRaceCulture}
#| label: career-status-by-race-plot
#| fig-alt: "Descending frequency barplot of the responses by race and/or culture to the following question: 'Roughly speaking, what is your career status?'"

contingencyPlot(
  df = visMain,
  contingX = "careerStatus",
  contingGrp = "raceCulture",
  colours = ostColours2rev
  )

```

---

##### disability and/or neurodivergence

```{r careerStatusByDisability}
#| label: career-status-by-disability-plot
#| fig-alt: "Descending frequency barplot of the responses by disability and/or neurodivergence to the following question: 'Roughly speaking, what is your career status?'"

contingencyPlot(
  df = visMain,
  contingX = "careerStatus",
  contingGrp = "disability",
  colours = ostColours2rev
  )

```

---

##### English as dominant language

```{r careerStatusByLangDomEng}
#| label: career-status-by-domLang-plot
#| fig-alt: "Descending frequency barplot of the responses by whether the participants were dominant in written English to the following question: 'Roughly speaking, what is your career status?'"

contingencyPlot(
  df = visMain,
  contingX = "careerStatus",
  contingGrp = "domLangEnglish",
  colours = ostColours2rev
  )

```

---

### type of engagement with *PsychoPy*<sup>&reg;</sup>

This section summarises, both visually and verbally, the responses to the following prompt:

>`r get_label(visMain$engagement)`

Participants had to choose from one of the following:

- *Occasional user*\
- *Frequent user*\
- *Occasional contributor*\
- *Frequent contributor*\
- *Senior developer*

#### everyone

The visualisation below presents responses in descending order of frequency.

```{r plotEngagement}
#| label: engagement-type-plot-everyone
#| fig-alt: "Descending frequency barplot of everyone's responses to the following question: 'What best describes your role/usage of PsychoPy?'"

visMain |>
  select(engagement) |>
  ostFreqPlot(
    ostColour = ostOrange, 
    sorting = "desc"
    )

```

##### verbal summary

The verbal summaries below proceed in the order in which the responses appeared in the original survey (i.e., not descending order of response frequency, as in the visualisation above).

With respect to the `r length(which(!is.na(visMain$engagement)))` participants who provided an answer to the question regarding roughly how they engage with *PsychoPy/JS*<sup>&reg;</sup>, the number of people in each type are as follows:

- user\
  - occasional: `r length(which(visMain$engagement == "Occasional user"))`, or `r round(length(which(visMain$engagement == "Occasional user"))/length(which(!is.na(visMain$engagement))),3)*100`%\
  - frequent: `r length(which(visMain$engagement == "Frequent user"))`, or `r round(length(which(visMain$engagement == "Frequent user"))/length(which(!is.na(visMain$engagement))),3)*100`%\

- contributor\
  - occasional: `r length(which(visMain$engagement == "Occasional contributor"))`, or `r round(length(which(visMain$engagement == "Occasional contributor"))/length(which(!is.na(visMain$engagement))),3)*100`%\
  - frequent: `r length(which(visMain$engagement == "Frequent contributor"))`, or `r round(length(which(visMain$engagement == "Frequent contributor"))/length(which(!is.na(visMain$engagement))),3)*100`%\

- senior developer: `r length(which(visMain$engagement == "Senior developer"))`, or `r round(length(which(visMain$engagement == "Senior developer"))/length(which(!is.na(visMain$engagement))),3)*100`%

##### [some remarks]

- just over 88% of the people who responded are users, not contributors\
- almost all of the others were *occasional contributors*\
- but about 2.2% were *frequent contributors* or *senior developers*


#### interactions

##### gender

```{r reorderFactors}

visMain$engagement <- fct_relevel(
  visMain$engagement,
  "Occasional user",
  "Frequent user",
  "Occasional contributor",
  "Frequent contributor",
  "Senior developer"
  )

visMain <- visMain |>
  var_labels(
    engagement = 
      "What best describes your role/usage of PsychoPy? (Note: 'Contributor' refers to any form of contribution, whether to the code, the documentation or supporting other users)"
  )

```


```{r engagementStatusByGender}
#| label: engagement-type-plot-gender
#| fig-alt: "Descending frequency barplot of responses by gender to the following question: 'What best describes your role/usage of PsychoPy?'"

contingencyPlot(
  df = visMain,
  contingX = "engagement",
  contingGrp = "gender",
  colours = ostColours3
  )

```


---

##### sexuality

```{r engagementStatusBySexuality}
#| label: engagement-type-plot-sexuality
#| fig-alt: "Descending frequency barplot of responses by sexual orientation to the following question: 'What best describes your role/usage of PsychoPy?'"

contingencyPlot(
  df = visMain,
  contingX = "engagement",
  contingGrp = "nonHeteroCommunity",
  colours = ostColours2rev
  )

```

---


##### race and/or culture

```{r engagementStatusByRaceCulture}
#| label: engagement-type-plot-race
#| fig-alt: "Descending frequency barplot of responses by race and/or culture to the following question: 'What best describes your role/usage of PsychoPy?'"

contingencyPlot(
  df = visMain,
  contingX = "engagement",
  contingGrp = "raceCulture",
  colours = ostColours2rev
  )

```

---

##### disability and/or neurodivergence

```{r engagementStatusByDisability}
#| label: engagement-type-plot-disability
#| fig-alt: "Descending frequency barplot of responses by disability and/or neurodivergence to the following question: 'What best describes your role/usage of PsychoPy?'"

contingencyPlot(
  df = visMain,
  contingX = "engagement",
  contingGrp = "disability",
  colours = ostColours2rev
  )

```

---

##### English as dominant language

```{r engagementStatusByEnglishDom}
#| label: engagement-type-plot-domLang
#| fig-alt: "Descending frequency barplot of responses by whether the participants are dominant in written English to the following question: 'What best describes your role/usage of PsychoPy?'"

contingencyPlot(
  df = visMain,
  contingX = "engagement",
  contingGrp = "domLangEnglish",
  colours = ostColours2rev
  )

```

---

### ways of contributing

This was a select-all-that-apply question, worded as follows:

>In which way do you contribute most? (select all that apply)

Each participant could select more than one option when describing how they contribute most. For ease of visual and verbal summary, the responses were converted into new variables, one per response. It is important to note here that multiple responses from the same person were possible here (and certainly did occur).

The possible selections were as follows:

- *Improving documentation*\
- *Supporting other users (e.g., on the forum)*\
- *Fixing bugs*\
- *Adding new features*\
- *Providing translations to other languages*\
- *Other (describe)*

It is important to keep in mind that participants may be counted as *yes* or *no* independently in any of the possible responses, which were converted to individual boolean variables below. If they selected the response, we assigned the value *selected*; if they did not, we assigned the value *not selected*. 

```{r importContributionsLong}

contributeLong <- readRDS("contributeLong.rds")

```


#### everyone

```{r contributionsEveryone}
#| label: contribEveryone-plot
#| fig-alt: "Frequency barplot of the selections made in response to the following question: 'In which way do you contribute most?'"

contributeLong |>
  drop_na(selected) |>
  wrappedFreqPlot(
    xVar = "selected",
    fillVar = "selected",
    wrapVar = "contributionType",
    ostColours = ostColours2rev
  )

```

##### descriptions

The participants were given the option to describe those other contributions. These descriptions are listed in the table below.

```{r tableOfOtherContributions}
#| label: other-contributions-table
#| tbl-cap: "Descriptions of other contributions to PyschoPy/JS that some participants provided"

visMain |> 
  select(contribOtherDesc) |>
  drop_na() |>
  datatable(
    class = 'cell-border stripe',
    colnames = "[I] contribute in these other ways"
  )

```


##### verbal summary

>`r get_label(visMain$contribImprvDoc)`

`r str_to_title(numbers_to_words(length(which(visMain$contribImprvDoc == 1))))`, or `r round(length(which(visMain$contribImprvDoc == 1))/length(which(!is.na(visMain$contribImprvDoc))),3)*100`% of those who responded to this question, indicated that they improved documentation.

---

>`r get_label(visMain$contribSuppOthers)`

`r str_to_title(numbers_to_words(length(which(visMain$contribSuppOthers == 1))))`, or `r round(length(which(visMain$contribSuppOthers == 1))/length(which(!is.na(visMain$contribSuppOthers))),3)*100`% of those who responded to this question, indicated that they supported others.

---

>`r get_label(visMain$contribFixBugs)`

`r str_to_title(numbers_to_words(length(which(visMain$contribFixBugs == 1))))`, or `r round(length(which(visMain$contribFixBugs == 1))/length(which(!is.na(visMain$contribFixBugs))),3)*100`% of those who responded to this question, indicated that they fixed bugs.

---

>`r get_label(visMain$contribAddFeatures)`

`r str_to_title(numbers_to_words(length(which(visMain$contribAddFeatures == 1))))`, or `r round(length(which(visMain$contribAddFeatures == 1))/length(which(!is.na(visMain$contribAddFeatures))),3)*100`% of those who responded to this question, indicated that they added features.

---

>`r get_label(visMain$contribProvTransl)`

`r str_to_title(numbers_to_words(length(which(visMain$contribProvTransl == 1))))`, or `r round(length(which(visMain$contribProvTransl == 1))/length(which(!is.na(visMain$contribProvTransl))),3)*100`% of those who responded to this question, indicated that they provided translations.

---

>`r get_label(visMain$contribOther)`

`r str_to_title(numbers_to_words(length(which(visMain$contribOther == 1))))`, or `r round(length(which(visMain$contribOther == 1))/length(which(!is.na(visMain$contribOther))),3)*100`% of those who responded to this question, indicated that they contributed in other ways. 

##### [some remarks]

- supporting others seems to be the dominant form of contributing among the survey participants

---

#### interactions

##### gender

```{r contributionsByGender}
#| label: contrib-by-gender-plot
#| fig-alt: "Frequency barplot of the selections made by gender in response to the following question: 'In which way do you contribute most?'"

contributeLong |>
  drop_na(gender) |>
  wrappedFreqInteractionPlot(
    xVar = "selected",
    fillVar = "gender",
    wrapVar = "contributionType",
    ostColours = ostColours3
  )

```

---

##### sexuality

```{r contributionsBySexuality}
#| label: contrib-by-sexuality-plot
#| fig-alt: "Frequency barplot of the selections made by sexual orientation in response to the following question: 'In which way do you contribute most?'"

contributeLong |>
  drop_na(nonHeteroCommunity) |>
  wrappedFreqInteractionPlot(
    xVar = "selected",
    fillVar = "nonHeteroCommunity",
    wrapVar = "contributionType",
    ostColours = ostColours2rev
  )

```

---

##### gender

```{r contributionsByRaceCulture}
#| label: contrib-by-race-plot
#| fig-alt: "Frequency barplot of the selections made by race and/or culture in response to the following question: 'In which way do you contribute most?'"

contributeLong |>
  drop_na(raceCulture) |>
  wrappedFreqInteractionPlot(
    xVar = "selected",
    fillVar = "raceCulture",
    wrapVar = "contributionType",
    ostColours = ostColours2rev
  )

```

---

##### disability and/or neurodivergence

```{r contributionsByDisability}
#| label: contrib-by-disability-plot
#| fig-alt: "Frequency barplot of the selections made by disability and/or neurodivergence in response to the following question: 'In which way do you contribute most?'"

contributeLong |>
  drop_na(disability) |>
  wrappedFreqInteractionPlot(
    xVar = "selected",
    fillVar = "disability",
    wrapVar = "contributionType",
    ostColours = ostColours2rev
  )

```

---

##### English as dominant language

```{r contributionsByDomLangEnglish}
#| label: contrib-by-dominant-language-plot
#| fig-alt: "Frequency barplot of the selections made by whether one is dominant in written English in response to the following question: 'In which way do you contribute most?'"

contributeLong |>
  drop_na(domLangEnglish) |>
  wrappedFreqInteractionPlot(
    xVar = "selected",
    fillVar = "domLangEnglish",
    wrapVar = "contributionType",
    ostColours = ostColours2rev
  )

```

---


### deterrents to contributing

Participants were asked the following:

>To what extent do each of the following limit the amount you feel able to contribute to the PsychoPy project?

Below the question was a list of the following potential causes:

- *Lack of interest*\
- *Lack of time*\
- *Lack of knowledge on how to get started*\
- *Lack of coding skills*\
- *Not confident I would be welcomed by the community*\
- *Not aware contributing was possible*

Participants could rank each of these on a `1`-`5` Likert scale, where `1` indicated *not at all* and a `5` indicated *very much*.

This section summarises, both visually and verbally, the rankings that participants provided for each potential cause.

::: {.callout-note}
Note that on this `1`-`5` scale, the number `3` is directly in the middle of the scale, which can be interpreted as neither agreeing nor disagreeing. We set responses of `3` to the side of the stacked frequency barplots below, in yellow.

Also, the barplots are sorted along descending frequency of agreement. That is, the topmost barplot is the one with highest number of agreements, whereas the bottommost barplot is the one with the highest number of disagreements.
:::

#### everyone

```{r deterrentsEveryone}
#| label: deterrents-plot
#| fig-alt: "Stacked frequency barplots of the responses to: 'To what extent do each of the following limit the amount you feel able to contribute to the PsychoPy project?'"

visMain |>
  dplyr::select(starts_with("deterrents")) |>
  stackedFrequencies(
    colours = ostColours5,
    figTitle = "Deterrents to contributing for everyone"
    )

```

##### verbal summary

Below, we describe the numbers in the figure above, but in the order in which the items appeared in the survey.

- *`r get_label(visMain$deterrentsLackOfInterest)`*\
  - Total responses: `r length(which(!is.na(visMain$deterrentsLackOfInterest)))`\
  - Those who believed this was *not* the case: `r length(which(visMain$deterrentsLackOfInterest == 1))+length(which(visMain$deterrentsLackOfInterest == 2))`, or `r round((length(which(visMain$deterrentsLackOfInterest == 1))+length(which(visMain$deterrentsLackOfInterest == 2)))/length(which(!is.na(visMain$deterrentsLackOfInterest))),3)*100`%\
  - Those who believed this *was* the case: `r length(which(visMain$deterrentsLackOfInterest == 4))+length(which(visMain$deterrentsLackOfInterest == 5))`, or `r round((length(which(visMain$deterrentsLackOfInterest == 4))+length(which(visMain$deterrentsLackOfInterest == 5)))/length(which(!is.na(visMain$deterrentsLackOfInterest))),3)*100`%\
  - Those who were neutral: `r length(which(visMain$deterrentsLackOfInterest == 3))`, or `r round(length(which(visMain$deterrentsLackOfInterest == 3))/length(which(!is.na(visMain$deterrentsLackOfInterest))),3)*100`%

- *`r get_label(visMain$deterrentsLackOfTime)`*\
  - Total responses: `r length(which(!is.na(visMain$deterrentsLackOfTime)))`\
  - Those who believed this was *not* the case: `r length(which(visMain$deterrentsLackOfTime == 1))+length(which(visMain$deterrentsLackOfTime == 2))`, or `r round((length(which(visMain$deterrentsLackOfTime == 1))+length(which(visMain$deterrentsLackOfTime == 2)))/length(which(!is.na(visMain$deterrentsLackOfTime))),3)*100`%\
  - Those who believed this *was* the case: `r length(which(visMain$deterrentsLackOfTime == 4))+length(which(visMain$deterrentsLackOfTime == 5))`, or `r round((length(which(visMain$deterrentsLackOfTime == 4))+length(which(visMain$deterrentsLackOfTime == 5)))/length(which(!is.na(visMain$deterrentsLackOfTime))),3)*100`%\
  - Those who were neutral: `r length(which(visMain$deterrentsLackOfTime == 3))`, or `r round(length(which(visMain$deterrentsLackOfTime == 3))/length(which(!is.na(visMain$deterrentsLackOfTime))),3)*100`%

- *`r get_label(visMain$deterrentsDontKnowHowToStart)`*\
  - Total responses: `r length(which(!is.na(visMain$deterrentsDontKnowHowToStart)))`\
  - Those who believed this was *not* the case: `r length(which(visMain$deterrentsDontKnowHowToStart == 1))+length(which(visMain$deterrentsDontKnowHowToStart == 2))`, or `r round((length(which(visMain$deterrentsDontKnowHowToStart == 1))+length(which(visMain$deterrentsDontKnowHowToStart == 2)))/length(which(!is.na(visMain$deterrentsDontKnowHowToStart))),3)*100`%\
  - Those who believed this *was* the case: `r length(which(visMain$deterrentsDontKnowHowToStart == 4))+length(which(visMain$deterrentsDontKnowHowToStart == 5))`, or `r round((length(which(visMain$deterrentsDontKnowHowToStart == 4))+length(which(visMain$deterrentsDontKnowHowToStart == 5)))/length(which(!is.na(visMain$deterrentsDontKnowHowToStart))),3)*100`%\
  - Those who were neutral: `r length(which(visMain$deterrentsDontKnowHowToStart == 3))`, or `r round(length(which(visMain$deterrentsDontKnowHowToStart == 3))/length(which(!is.na(visMain$deterrentsDontKnowHowToStart))),3)*100`%

- *`r get_label(visMain$deterrentsLackOfCodingSkills)`*\
  - Total responses: `r length(which(!is.na(visMain$deterrentsLackOfCodingSkills)))`\
  - Those who believed this was *not* the case: `r length(which(visMain$deterrentsLackOfCodingSkills == 1))+length(which(visMain$deterrentsLackOfCodingSkills == 2))`, or `r round((length(which(visMain$deterrentsLackOfCodingSkills == 1))+length(which(visMain$deterrentsLackOfCodingSkills == 2)))/length(which(!is.na(visMain$deterrentsLackOfCodingSkills))),3)*100`%\
  - Those who believed this *was* the case: `r length(which(visMain$deterrentsLackOfCodingSkills == 4))+length(which(visMain$deterrentsLackOfCodingSkills == 5))`, or `r round((length(which(visMain$deterrentsLackOfCodingSkills == 4))+length(which(visMain$deterrentsLackOfCodingSkills == 5)))/length(which(!is.na(visMain$deterrentsLackOfCodingSkills))),3)*100`%\
  - Those who were neutral: `r length(which(visMain$deterrentsLackOfCodingSkills == 3))`, or `r round(length(which(visMain$deterrentsLackOfCodingSkills == 3))/length(which(!is.na(visMain$deterrentsLackOfCodingSkills))),3)*100`%

- *`r get_label(visMain$deterrentsNotConfidentOfWelcome)`*\
  - Total responses: `r length(which(!is.na(visMain$deterrentsNotConfidentOfWelcome)))`\
  - Those who believed this was *not* the case: `r length(which(visMain$deterrentsNotConfidentOfWelcome == 1))+length(which(visMain$deterrentsNotConfidentOfWelcome == 2))`, or `r round((length(which(visMain$deterrentsNotConfidentOfWelcome == 1))+length(which(visMain$deterrentsNotConfidentOfWelcome == 2)))/length(which(!is.na(visMain$deterrentsNotConfidentOfWelcome))),3)*100`%\
  - Those who believed this *was* the case: `r length(which(visMain$deterrentsNotConfidentOfWelcome == 4))+length(which(visMain$deterrentsNotConfidentOfWelcome == 5))`, or `r round((length(which(visMain$deterrentsNotConfidentOfWelcome == 4))+length(which(visMain$deterrentsNotConfidentOfWelcome == 5)))/length(which(!is.na(visMain$deterrentsNotConfidentOfWelcome))),3)*100`%\
  - Those who were neutral: `r length(which(visMain$deterrentsNotConfidentOfWelcome == 3))`, or `r round(length(which(visMain$deterrentsNotConfidentOfWelcome == 3))/length(which(!is.na(visMain$deterrentsNotConfidentOfWelcome))),3)*100`%

- *`r get_label(visMain$deterrentsUnawareContributingWasPossible)`*\
  - Total responses: `r length(which(!is.na(visMain$deterrentsUnawareContributingWasPossible)))`\
  - Those who believed this was *not* the case: `r length(which(visMain$deterrentsUnawareContributingWasPossible == 1))+length(which(visMain$deterrentsUnawareContributingWasPossible == 2))`, or `r round((length(which(visMain$deterrentsUnawareContributingWasPossible == 1))+length(which(visMain$deterrentsUnawareContributingWasPossible == 2)))/length(which(!is.na(visMain$deterrentsUnawareContributingWasPossible))),3)*100`%\
  - Those who believed this *was* the case: `r length(which(visMain$deterrentsUnawareContributingWasPossible == 4))+length(which(visMain$deterrentsUnawareContributingWasPossible == 5))`, or `r round((length(which(visMain$deterrentsUnawareContributingWasPossible == 4))+length(which(visMain$deterrentsUnawareContributingWasPossible == 5)))/length(which(!is.na(visMain$deterrentsUnawareContributingWasPossible))),3)*100`%\
  - Those who were neutral: `r length(which(visMain$deterrentsUnawareContributingWasPossible == 3))`, or `r round(length(which(visMain$deterrentsUnawareContributingWasPossible == 3))/length(which(!is.na(visMain$deterrentsUnawareContributingWasPossible))),3)*100`%

##### central tendency

```{r tableDeterrents}
#| label: deterrents-stats-table
#| tbl-cap: "Statistical summaries of responses to statements regarding deterrents to contributing."
#| output: asis

visMain |>
  select(starts_with("deterrents"))  |>
  tableLikert(
    lowerBound = "1 = not at all",
    upperBound = "5 = very much"
  )

```



<!-- Combined with the fact that many of these responses are coming from frequent and occasional users (vs. contributors), this is both unsurprising and promising for the purposes of our survey, I think... except *lack of time* -->


##### [some remarks]

- *Lack of time* is dominant here\
- but *not knowing how to start* is close behind, which is good news for us in terms of increasing the contributor base\
- importantly, most participants disagreed that *lack of interest* or *lack of confidence in a welcome* were holding them back

#### interactions


```{r importDeterrentsLong}

deterrentsLong <- readRDS("deterrentsLong.rds")
deterrentsLabel <- get_label(deterrentsLong$deterrent)

```

##### gender

```{r plotDeterrentsLikertByGender}
#| label: deterrents-likert-plot-by-gender
#| fig-alt: "Boxplots of responses by gender to the the following question: 'To what extent do each of the following limit the amount you feel able to contribute to the PsychoPy project?.'" 

intLabel <- "Gender"
deterrentsLong |>
  select(gender, deterrent, response) |>
  drop_na(gender) |>
  drop_na(deterrent) |>
  drop_na(response) |>
  boxplotWithInteraction(
    xVar = "response",
    yVar = "gender",
    wrapVar = "deterrent",
    ostColours = ostColours3,
    xLabel = deterrentsLabel,
    fillLabel = intLabel,
    figCaption = "Notes: \n1. A response of 1 indicates 'not at all' \n2. A response of 5 indicates 'very much'\n3. The mean is represented by the diamond"
    )

```

```{r deterrentsByGender}

visMain |>
  dplyr::select(starts_with("deterrents"), gender) |>
  group_by(gender) |>
  stackedFrequencies(colours=ostColours5)

```

---

##### sexual orientation

```{r deterrentsBySexuality}

visMain |>
  dplyr::select(starts_with("deterrents"), nonHeteroCommunity) |>
  group_by(nonHeteroCommunity) |>
  stackedFrequencies(colours=ostColours5)

```

---

##### race and/or culture

```{r deterrentsByRaceCulture}

visMain |>
  dplyr::select(starts_with("deterrents"), raceCulture) |>
  group_by(raceCulture) |>
  stackedFrequencies(colours=ostColours5)

```

---

##### disability and/or neurodivergence

```{r deterrentsByDisability}

visMain |>
  dplyr::select(starts_with("deterrents"), disability) |>
  group_by(disability) |>
  stackedFrequencies(colours=ostColours5)

```

---

##### English as dominant language

```{r deterrentsByDomLangEnglish}

visMain |>
  dplyr::select(starts_with("deterrents"), domLangEnglish) |>
  group_by(domLangEnglish) |>
  stackedFrequencies(colours=ostColours5)

```


---

### workshops on contributing

This section summarises, both visually and verbally, the answer to the following question:

>`r get_label(visMain$workshopsOnContributing)`

Participants provided answers on a `1`-`5` Likert scale, where `1` indicated *Strongly disagree* and a `5` indicated *Strongly agree*.

#### everyone

```{r workshopLabels}

workshopLabel <- get_label(visMain$workshopsOnContributing)
likertValues <- get_labels(visMain$workshopsOnContributing)

```


```{r importWorkshopLong }

workshopLong <- readRDS("workshopLong.rds")

```

```{r plotWorkshopsOnContributing}
#| label: contrib-workshops-plot
#| fig-alt: "Barplot of responses to the following statement: 'My engagement with the community would be helped if workshops were provided on how to contribute'"

workshopLong |> 
  select(workshopsOnContributing) |> 
  ostFreqPlot(
    ostColour = ostYellow,
    sorting = "none"
  )

```

#### verbal summary

Below, we describe the numbers in the figure above.

- *`r get_label(visMain$workshopsOnContributing)`*\
  - Total responses: `r length(which(!is.na(visMain$workshopsOnContributing)))`\
  - Those who *strongly disagreed* (`1`): `r length(which(visMain$workshopsOnContributing == 1))`, or `r round(length(which(visMain$workshopsOnContributing == 1))/length(which(!is.na(visMain$workshopsOnContributing))),3)*100`%\
  - Those who somewhat *disagreed* (`2`): `r length(which(visMain$workshopsOnContributing == 2))`, or `r round(length(which(visMain$workshopsOnContributing == 2))/length(which(!is.na(visMain$workshopsOnContributing))),3)*100`%\
  - Those who were neutral (`3`): `r length(which(visMain$workshopsOnContributing == 3))`, or `r round(length(which(visMain$workshopsOnContributing == 3))/length(which(!is.na(visMain$workshopsOnContributing))),3)*100`%\
  - Those who somewhat *agreed* (`4`): `r length(which(visMain$workshopsOnContributing == 4))`, or `r round(length(which(visMain$workshopsOnContributing == 4))/length(which(!is.na(visMain$workshopsOnContributing))),3)*100`%\
  - Those who *strongly agreed* (`5`): `r length(which(visMain$workshopsOnContributing == 5))`, or `r round(length(which(visMain$workshopsOnContributing == 5))/length(which(!is.na(visMain$workshopsOnContributing))),3)*100`%\

#### central tendency

```{r}
#| label: workshops-stats-table
#| tbl-cap: "Statistical summaries of responses to statement regarding the potential helpfulness of contributor workshops."
#| output: asis

visMain |>
  select(workshopsOnContributing)  |>
  tableLikert(
    lowerBound = "1 = Strongly disagree",
    upperBound = "5 = Strongly agree"
  )

```

#### [some remarks]

- It looks like around half of the participants agreed that they could be engaged more with workshops. That's really good.

### interactions

#### gender

```{r plotWkShpsLikertByGender}
#| label: workshop-likert-plot-by-gender
#| fig-alt: "Boxplots of responses by gender to the question regarding whether the participant felt there engagement would increase with contributor workshops." 

legendLabel <- "Gender"
visMain |>
  select(gender, workshopsOnContributing) |>
  drop_na(gender) |>
  drop_na(workshopsOnContributing) |>
  boxplotWithInteraction(
    xVar = "workshopsOnContributing",
    yVar = "gender",
    lowerBound = 1,
    upperBound = 5,
    ostColours = ostColours3,
    xLabel = workshopLabel,
    fillLabel = legendLabel,
    tickLabels = likertValues,
    pointFill = "darkgrey",
    wrapVar = NULL,
    figCaption = "Notes: \n1. A response of 1 indicates 'Strongly disagree' \n2. A response of 5 indicates 'Strongly agree'\n3. The mean is represented by the diamond"
    )

```

---

#### other EDI variables


```{r plotWkShpsLikertByOtherEDIs}
#| label: workshop-likert-plot-by-other-edis
#| fig-alt: "Boxplots of responses by EDI variables other than gender to the question regarding whether the participant felt there engagement would increase with contributor workshops." 

legendLabel <- "Member\nof group"
workshopLong |>
  drop_na(workshopsOnContributing) |>
  drop_na(response) |>
  boxplotWithInteraction(
    xVar = "workshopsOnContributing",
    yVar = "response",
    lowerBound = 1,
    upperBound = 5,
    ostColours = ostColours2rev,
    xLabel = workshopLabel,
    fillLabel = legendLabel,
    tickLabels = likertValues,
    pointFill = "#F7F11C",
    wrapVar = "ediVar",
    figCaption = "Notes:\n1. A response of 1 indicates 'Strongly disagree'\n2. A response of 5 indicates 'Strongly agree'\n3. The mean is represented by the diamond"
  )

```

---

## *Code of Conduct* and documentation

The third group of items on the survey collected information about documentation and the participants' awareness of and experience with the [Code of Conduct](https://github.com/psychopy/psychopy/blob/dev/code-of-conduct.md).

There were three questions concerning each of the following:

- awareness of the *Code of Conduct*\
- how findable, searchable, and accessible *PsychoPy*'s<sup>&reg;</sup> documentation is\
- how much they trust the *Code of Conduct* will be enforced

The first was answered with a simple *yes* or *no*. The latter two were statements evaluated with a `1`-`7` Likert scale, where `1` represented *Strongly disagree*, and `7` represented *Strongly agree*.

::: {.callout-note}
As before, note that on the `1`-`7` scale, the number `4` is directly in the middle of the scale, which can be interpreted as neither agreeing nor disagreeing. Accordingly, we set responses of `4` to the side of the respective stacked frequency barplots, in yellow.
:::

### awareness

The sections directly below summarise, both visually and verbally, the answer to the following question:

>`r get_label(visMain$awareOfCodeOfConduct)`

#### everyone

```{r plotCodeOfConduct}
#| label: codeofconduct-plot
#| fig-alt: "Frequency barplot of responses to the following question: 'I am aware of the community Code of Conduct' If participants chose to respond, they could respond with either 'yes' or 'no.'"

visMain |> 
  select(awareOfCodeOfConduct) |> 
  ostFreqPlot(
    ostColour = ostOrange,
    sorting = "none"
  )

```

#### verbal summary

- *`r get_label(visMain$awareOfCodeOfConduct)`*\
  - Total responses: `r length(which(!is.na(visMain$awareOfCodeOfConduct)))` (out of `r nrow(visMain)`)  or `r round(length(which(!is.na(visMain$awareOfCodeOfConduct)))/nrow(visMain),3)*100`% of the total\
  - Those who selected ***no***: `r length(which(visMain$awareOfCodeOfConduct == 0))`, or `r round(length(which(visMain$awareOfCodeOfConduct == 0))/length(which(!is.na(visMain$awareOfCodeOfConduct))),3)*100`%\
  - Those who selected ***yes***: `r length(which(visMain$awareOfCodeOfConduct == 1))`, or `r round(length(which(visMain$awareOfCodeOfConduct == 1))/length(which(!is.na(visMain$awareOfCodeOfConduct))),3)*100`%

---

#### interactions

##### gender

```{r codeOfConductAwarenessByGender}
#| label: codeofconduct-awareness-by-gender-plot
#| fig-alt: "Contingency barplot of responses by gender to the following question: 'I am aware of the community Code of Conduct' If participants chose to respond, they could respond with either 'yes' or 'no.'"

contingencyPlot(
  df = visMain,
  contingX = "awareOfCodeOfConduct",
  contingGrp = "gender",
  colours = ostColours3
  )

```

---

##### sexuality

```{r codeOfConductAwarenessBySexuality}
#| label: codeofconduct-awareness-by-sexuality-plot
#| fig-alt: "Contingency barplot of responses by sexual orientation to the following question: 'I am aware of the community Code of Conduct' If participants chose to respond, they could respond with either 'yes' or 'no.'"

contingencyPlot(
  df = visMain,
  contingX = "awareOfCodeOfConduct",
  contingGrp = "nonHeteroCommunity",
  colours = ostColours2rev
  )

```

##### race and/or culture

```{r codeOfConductAwarenessByRace}
#| label: codeofconduct-awareness-by-race-plot
#| fig-alt: "Contingency barplot of responses by race and/or culture to the following question: 'I am aware of the community Code of Conduct' If participants chose to respond, they could respond with either 'yes' or 'no.'"

contingencyPlot(
  df = visMain,
  contingX = "awareOfCodeOfConduct",
  contingGrp = "raceCulture",
  colours = ostColours2rev
  )

```

##### disability and/or neurodivergence

```{r codeOfConductAwarenessByDisability}
#| label: codeofconduct-awareness-by-disability-plot
#| fig-alt: "Contingency barplot of responses by disability and/or neurodivergence to the following question: 'I am aware of the community Code of Conduct' If participants chose to respond, they could respond with either 'yes' or 'no.'"

contingencyPlot(
  df = visMain,
  contingX = "awareOfCodeOfConduct",
  contingGrp = "disability",
  colours = ostColours2rev
  )

```

##### English as dominant language

```{r codeOfConductAwarenessByDomLang}
#| label: codeofconduct-awareness-by-domlang-plot
#| fig-alt: "Contingency barplot of responses by whether English is the respondent's dominant written language to the following question: 'I am aware of the community Code of Conduct' If participants chose to respond, they could respond with either 'yes' or 'no.'"

contingencyPlot(
  df = visMain,
  contingX = "awareOfCodeOfConduct",
  contingGrp = "domLangEnglish",
  colours = ostColours2rev
  )

```

### findability, searchability, & accessibility

The sections directly below summarise, both visually and verbally, the answer to the following question:

>`r get_label(visMain$psychopyDocumentationEasy)`

#### everyone

```{r plotDocEasy}
#| warning: false
#| label: find-doceasy-plot
#| fig-alt: "Barplot of agreement responses to the statement regarding findability, searchability, and accessibility of documentation."

visMain |>
  select(psychopyDocumentationEasy) |>
  ostFreqPlot(
    ostColour = ostOrange,
    sorting = "none"
  )

```

#### verbal summary

- *`r get_label(visMain$psychopyDocumentationEasy)`*\
  - Total responses: `r length(which(!is.na(visMain$psychopyDocumentationEasy)))` (out of `r nrow(visMain)`)  or `r round(length(which(!is.na(visMain$psychopyDocumentationEasy)))/nrow(visMain),3)*100`% of the total\
  - Those who selected `1` (*Strongly disagree*): `r length(which(visMain$psychopyDocumentationEasy == 1))`, or `r round(length(which(visMain$psychopyDocumentationEasy == 1))/length(which(!is.na(visMain$psychopyDocumentationEasy))),3)*100`%\
  - Those who selected `2`: `r length(which(visMain$psychopyDocumentationEasy == 2))`, or `r round(length(which(visMain$psychopyDocumentationEasy == 2))/length(which(!is.na(visMain$psychopyDocumentationEasy))),3)*100`%\
  - Those who selected `3`: `r length(which(visMain$psychopyDocumentationEasy == 3))`, or `r round(length(which(visMain$psychopyDocumentationEasy == 3))/length(which(!is.na(visMain$psychopyDocumentationEasy))),3)*100`%\
  - Those who selected `4` (neutral): `r length(which(visMain$psychopyDocumentationEasy == 4))`, or `r round(length(which(visMain$psychopyDocumentationEasy == 4))/length(which(!is.na(visMain$psychopyDocumentationEasy))),3)*100`%\
  - Those who selected `5`: `r length(which(visMain$psychopyDocumentationEasy == 5))`, or `r round(length(which(visMain$psychopyDocumentationEasy == 5))/length(which(!is.na(visMain$psychopyDocumentationEasy))),3)*100`%\
  - Those who selected `6`: `r length(which(visMain$psychopyDocumentationEasy == 6))`, or `r round(length(which(visMain$psychopyDocumentationEasy == 6))/length(which(!is.na(visMain$psychopyDocumentationEasy))),3)*100`%\
  - Those who selected `7` (*Strongly agree*): `r length(which(visMain$psychopyDocumentationEasy == 7))`, or `r round(length(which(visMain$psychopyDocumentationEasy == 7))/length(which(!is.na(visMain$psychopyDocumentationEasy))),3)*100`%

### trust in enforcement

The sections directly below summarise, both visually and verbally, the answer to the following question:

>`r get_label(visMain$trustCodeWillBeEnforced)`

#### visualisation

```{r plotTrustCodeEnforced}
#| warning: false
#| label: trust-enforcement-plot
#| fig-alt: "Barplot of agreement responses to the statement regarding trust in enforcement of the Code of Conduct."

visMain |> 
  select(trustCodeWillBeEnforced) |> 
  ostFreqPlot(
    ostColour = ostYellow,
    sorting = "none"
  )

```

#### verbal summary

- *`r get_label(visMain$trustCodeWillBeEnforced)`*\
  - Total responses: `r length(which(!is.na(visMain$trustCodeWillBeEnforced)))` (out of `r nrow(visMain)`)  or `r round(length(which(!is.na(visMain$trustCodeWillBeEnforced)))/nrow(visMain),3)*100`% of the total\
  - Those who selected `1` (*Strongly disagree*): `r length(which(visMain$trustCodeWillBeEnforced == 1))`, or `r round(length(which(visMain$trustCodeWillBeEnforced == 1))/length(which(!is.na(visMain$trustCodeWillBeEnforced))),3)*100`%\
  - Those who selected `2`: `r length(which(visMain$trustCodeWillBeEnforced == 2))`, or `r round(length(which(visMain$trustCodeWillBeEnforced == 2))/length(which(!is.na(visMain$trustCodeWillBeEnforced))),3)*100`%\
  - Those who selected `3`: `r length(which(visMain$trustCodeWillBeEnforced == 3))`, or `r round(length(which(visMain$trustCodeWillBeEnforced == 3))/length(which(!is.na(visMain$trustCodeWillBeEnforced))),3)*100`%\
  - Those who selected `4` (neutral): `r length(which(visMain$trustCodeWillBeEnforced == 4))`, or `r round(length(which(visMain$trustCodeWillBeEnforced == 4))/length(which(!is.na(visMain$trustCodeWillBeEnforced))),3)*100`%\
  - Those who selected `5`: `r length(which(visMain$trustCodeWillBeEnforced == 5))`, or `r round(length(which(visMain$trustCodeWillBeEnforced == 5))/length(which(!is.na(visMain$trustCodeWillBeEnforced))),3)*100`%\
  - Those who selected `6`: `r length(which(visMain$trustCodeWillBeEnforced == 6))`, or `r round(length(which(visMain$trustCodeWillBeEnforced == 6))/length(which(!is.na(visMain$trustCodeWillBeEnforced))),3)*100`%\
  - Those who selected `7` (*Strongly agree*): `r length(which(visMain$trustCodeWillBeEnforced == 7))`, or `r round(length(which(visMain$trustCodeWillBeEnforced == 7))/length(which(!is.na(visMain$trustCodeWillBeEnforced))),3)*100`%\

#### central tendency

```{r tableOfCodeOfConductStats}
#| label: codeofconduct-stats-table
#| tbl-cap: "Statistics for responses to statements regarding the Code of Conduct and documentation"
#| output: asis

visMain |>
  select(c("psychopyDocumentationEasy", "trustCodeWillBeEnforced")) |> 
  tableLikert(
    lowerBound = "1 = Strongly disagree",
    upperBound = "7 = Strongly agree"
  )

```

### [some remarks]

- About two-thirds of the participants were aware of the *Code of Conduct*. I suppose that's to be expected, but it's kinda disappointing, no?\
- Most of them felt that the documentation was *easily findable, searchable, and accessible*. But there were a few (just under 20%) who disagreed with this in general.\
- In terms of trust that the *Code of Conduct* would be enforced, there was general agreement here, though about 5% expressed mild disagreement here. About 2% expressed somewhat stronger disagreement. One person expressed the strongest level of disagreement (i.e., *Strongly disagree*).

# [some final remarks]

## background variables

In terms of the background variables, most of the people responding were early-career researchers and frequent users. Most of them interact with the community through helping others on the forum.

*Lack of time* and *not knowing how to start* seem to be the most important deterrents, but certainly not lack of interest or fear of not being welcome in the community. About half of them agreed that workshops would encourage them to contribute more.

## EDI variables

With respect to equity, diversity, and inclusion, there were several interesting findings.

### gender

Concerning *gender*, there was an odd finding at first blush. None of the eight people who identified as *neither* a man *nor* a woman indicated that they felt their identity had affected their interactions in the *PsychoPy*<sup>&reg;</sup> community. However, two people who identified as men and two who identified as women did. Note that we did not ask anyone whether they were transgender. Any number of the 4 women and men could have been transgender.

But looking at the issues of *treatment*, *self-regard*, and *isolation*, this group seemed to be in general disagreement with (or neutral about) almost all of the statements. Still, on each question, about 1 out of the 4 seems to indicate some level of agreement. This could be more than one person.

### sexual orientation

The next category was *sexual orientation*. Here, only $\frac{1}{36}$ indicated that their sexual orientation might have been a problem in the *PsychoPy*<sup>&reg;</sup> community. Still, that one person indicated disagreement with all of the *treatment* and *self-regard* questions. The only question that they weren't in disagreement about was the *isolation* statement, and even there, they were neutral (having selected `4` on the `1`-`7` scale).

### race and/or culture

Next we come to *race* and/or *culture*. Here, only $\frac{3}{42}$ felt that their identity had affected their interactions with the *PsychoPy*<sup>&reg;</sup> community.

In general however, they were fairly split across the board in terms of how others had treated them. Two exceptions were *negative perception by others*, where two of the three expressed that they had experienced that, and *intentially derisive comments*, where no one expressed agreement with having experienced that.

They were however, (almost) overwhelmingly in agreement with the *self-regard* and *isolation* statements.

They seem to lack confidence, more than anything.

### disability and/or neurodivergence

With respect to *disability* and/or *neurodivergence*, the highest percentage of all the groups ($\frac{6}{28}$) went on to evaluate the subsequent EDI statements.

This group disagreed more unanimously with the *treatment* statements, with only one of them indicating that (1) there had some any negative perception of them, and (2) that they felt they needed to hide their identity in this regard.

But on the *self-regard* and *isolation* statements, there was general agreement. They seem to lack some self-confidence, along with feeling a little isolated.

### written language dominance

Concerning *written language dominance*, of the 82 participants who indicated that their dominant written language is not English, only nine suggested that this might have been a problem in their interactions with the *PsychoPy*<sup>&reg;</sup> community.

Among them, they disagreed in general (but not universally) with the statements regarding poor treatment by others. If there were any statements that raise concern, they are the ones about negative perception and hiding their identity (similar to the other groups).

But unlike the race/culture and disability/neurodivergence groups, this group also expressed little agreement with the *self-regard* statements. This actually makes sense as there's little reason to believe that non-English language dominance should affect one's self-regard.

In their case, the stand-out statement was the one on isolation. The majority of them do feel isolated, quite strongly it seems.

## *Code of Conduct* & *documentation* variables

With respect to the *Code of Conduct* and *documentation*, a sizeable minority was not aware of the existence of the *Code of Conduct*. There was general (but not overwhelming) agreement that the documentation was easily *findable, searchable, and accessible* (*M* = 4.8, *SD* = 1.45, negative skew). There quite  strong agreement that the *Code of Conduct* would be enforced (*M* = 5.4, *SD* = 1.32, strong negative skew with responses stacked increasingly positive).

---

# Color-blindness check

The custom palettes used in this report (which are based on the colors used at [Open Science Tools, Ltd.](https://opensciencetools.org/)) are simulated through various forms of color blindness below to ensure that most people can distinguish the colors on the figures.

## two colors

```{r colorblindnessCheckOst2}

palette_bivariate_plot(ostColours2)
palette_check(ostColours2)

```

## three colors

```{r colorblindnessCheckOst3}

palette_bivariate_plot(ostColours3)
palette_check(ostColours3)

```

## five colors

```{r colorblindnessCheckOst5}

palette_bivariate_plot(ostColours5)

```

## six colors

```{r colorblindnessCheckOst6}

palette_bivariate_plot(ostColours6)
palette_check(ostColours6)

```

# *R* Packages used

```{r citePackages}
#| results: asis

allPackages <- 
  append(
    neededPackages,
    c(
      "grateful", 
      "remotes",
      "gghalves"
      )
    )

    pkgs <- grateful::cite_packages(
      pkgs = allPackages,
      output = "table", 
      cite.tidyverse = F,
      bib.file = "grateful-refs-sumandvis.bib",
      Rmd.file = "grateful-report-sumandvis.Rmd",
      out.name = "grateful-citations-sumandvis"
      )
    knitr::kable(pkgs)

```


