---
title: "Github Data Summary"
format: html
---

## Introduction

To parallel our survey, we wanted to also observe if any changes were observed in the GitHub data itself. We therefore assessed pull request activity (number of PRs opened, merged, and closed), the nature of pull requests (including size (number of lines changed) and type, labeled as follows: BF – Bug Fix, FF – Feature Fix, RF – Refactor, NF – New Feature, ENH – Enhancement to existing code, DOC – Documentation, TEST – Adding or modifying tests, or unlabeled), contributor engagement (number of active contributors, new vs returning contributors, and PRs per contributor), and PR dynamics (time to merge and number of comments), disaggregated by contributor type (staff vs external). We chose two windows to analyse these factors: Window 1: 28 May 2022 – 27 Nov 2022, Window 2: 28 May 2024 – 27 Nov 2024, thus each window was sampled 6 months prior to the dissemination of each survey. These windows were selected to give equal length at each timepoint, whilst also allowing a wide enough window to capture meaningful activity and avoiding seasonal mismatches between sampling points.

## Analysis and Results

Data were pulled from the PsychoPy github repository https://github.com/psychopy/psychopy from two time windows Window 1: 28 May 2022 – 27 Nov 2022, Window 2: 28 May 2024 – 27 Nov 2024. We identified github author names known to be internal staff to Open Science Tools (the social enterprise maintaining PsychoPy), so that we could seperately analyse External and Staff contributions.

```{r setup-libraries, include=FALSE}
library(dplyr)
library(lubridate)
library(ggplot2)
library(readr)
library(tidyr)
library(stringr)   # make sure this is loaded
library(dplyr)
library(knitr)
library(kableExtra)
library("readxl")
library(glue)


dir.create("github_plots", showWarnings = FALSE)
```

```{r load-and-prepare-data, include=FALSE}
# Load staff list
staff_authors <- c("suelynnmah", "TEParsons", "mdcutone", "peircej", 
                   "isolver", "RebeccaHirst", "lightest", "kimDundas")  

# Load CSVs for both windows
pr_window1 <- read_csv("data/psychopy_pull_requests_2022-05-28_to_2022-11-27_combined.csv")
pr_window2 <- read_csv("data/psychopy_pull_requests_2024-05-28_to_2024-11-27_combined.csv")

# Load manual label files
manual_2022 <- read_excel("data/manual_pr_labels_2022.xlsx")
manual_2024 <- read_excel("data/manual_pr_labels_2024.xlsx")

# Define the categories
categories <- c("BF", "FF", "RF", "NF", "ENH", "DOC", "TEST")

# Function to add Contribution Type column
add_contribution_type <- function(main_data, manual_data) {
  main_data %>%
    # First detect category from Title
    mutate(Category_from_title = str_extract(Title, paste0("^(", paste(categories, collapse="|"), ")")),
           # Merge manual labels based on PR Number
           PR_Number = as.character(`PR Number`)) %>%
    left_join(manual_data %>% mutate(PR_Number = as.character(`PR Number`)),
              by = "PR_Number") %>%
    # Decide final contribution type
    mutate(`Contribution_Type` = ifelse(!is.na(Category_from_title),
                                        Category_from_title,
                                        Label)) %>%
    select(-Category_from_title)
}

# Apply function to both datasets
pr_window1 <- add_contribution_type(pr_window1, manual_2022)
pr_window2 <- add_contribution_type(pr_window2, manual_2024)

# Add a window identifier
pr_window1 <- pr_window1 %>% mutate(Window = "Window 1")
pr_window2 <- pr_window2 %>% mutate(Window = "Window 2")

# Combine into one dataframe
pr_all <- bind_rows(pr_window1, pr_window2)

# Contributor type assignment
pr_all <- pr_all %>%
  mutate(Contributor_Type = ifelse(Author %in% staff_authors, "Staff", "External"))

```

### Pull Request Activity and Nature

We assessed Pull Request (PR) activity in each Time Window by Contributor Type (Staff vs. External). We also separated this by Merge status (Merged or Not Merged) and Contribution Type (BF – Bug Fix, FF – Feature Fix, RF – Refactor, NF – New Feature, ENH – Enhancement to existing code, DOC – Documentation, TEST – Adding or modifying tests, or unlabeled). The results are shown in Figure XXX, and exact figures shown in Supplementary Table S1. We also examined the size of Pull Requests (Full table Supplementary S2). 

At Time Window 2 there were more pull requests made by External contributors compared with Time Window 1. The nature of these PRs descriptively changed between time windows. At Time Window 1 most PRs from External contributors were Bug Fixes (BF), and no contributions were to changes in documentation (DOC). At Time Window 2, most PRs from External contributors were still Bug Fixes, but this was followed by 27 PRs that were documentation changes. Notably, many of these changes were to add translations to the software (in particular to Arabic, Spanish and Portuguese) - likely reflecting an impact of translator workshops hosted between time windows.   
Across the two time windows, Pull Request (PR) sizes were generally small, particularly for those that were merged. At Time Window 1, the median size of merged PRs was slightly smaller for External contributors (median = 10.5 lines, mean = 284.3, SD = 566.9) than for Staff contributors (median = 20.5 lines, mean = 1559.3, SD = 19,755.9), whereas non-merged PRs were larger for External contributors (median = 283 lines, mean = 66,954.6, SD = 148,865.5) than for Staff (median = 113 lines, mean = 1007.7, SD = 3,552.4). Notably, the high degree of variability in non merged PRs reflect the presence of large outlier changes. At Time Window 2, median PR sizes were more similar between contributor types (External = 17 lines, mean = 397.0, SD = 1,692.5; Staff = 21 lines, mean = 313.0, SD = 1,502.0), both for merged and non-merged PRs. The variability of PR size also reduced between time windows. Overall, these results suggest that between time windows the size of PR’s accepted to the repository from External and Staff contributors became more similar between time windows. This might also reflect the impact of events between time windows, such as workshops, which may have influenced the stylistic choice of external contributors in their PR activity. 


```{r pr-contributor-contribution-merge-plot, message=FALSE, warning=FALSE, echo=FALSE, fig.cap="Figure 1. Number of Pull Requests (PRs) made in Time Window 1 and 2. Results are shown for Merged PRs and seperated by Staff and External contributors. Stacked plots indicate contribution type. BF – Bug Fix, FF – Feature Fix, RF – Refactor, NF – New Feature, ENH – Enhancement to existing code, DOC – Documentation, TEST – Adding or modifying tests, NA - unlabeled"}
library(dplyr)
library(ggplot2)

# -----------------------
# Prepare data for plotting (Merged only) + combine FF with BF
# -----------------------
pr_activity_plot_data <- pr_all %>%
  filter(Merged == TRUE) %>%                                # keep only merged PRs
  mutate(Contribution_Type = if_else(Contribution_Type %in% c("BF","FF"),
                                     "BF/FF", Contribution_Type)) %>%  # combine BF & FF
  group_by(Window, Contributor_Type, Contribution_Type, Merged) %>%
  summarise(PR_Count = n(), .groups = "drop")

# -----------------------
# Colour mapping
# -----------------------
# BF/FF gets the old BF colour; ENH gets the old FF colour
contrib_cols <- c(
  "BF/FF" = "#fbe1d4",  # old BF colour
  "DOC"   = "#EB692A",
  "NF"    = "#7deaf6",
  "ENH"   = "#d4f8fc",  # old FF colour
  "TEST"  = "darkgrey",
  "RF"    = "#26DCF0"
)
present <- intersect(names(contrib_cols), unique(pr_activity_plot_data$Contribution_Type))
contrib_cols_use <- contrib_cols[present]

# -----------------------
# Plot PR activity (Merged only) with facets for Window
# -----------------------
pr_activity_plot <- ggplot(pr_activity_plot_data,
                           aes(x = Contributor_Type, y = PR_Count, fill = Contribution_Type)) +
  geom_bar(stat = "identity", position = "stack") +
  facet_grid(. ~ Window) +  # columns = Windows; no Merged row
  scale_fill_manual(values = contrib_cols_use, na.value = "lightgray") +
  theme_minimal() +
  labs(title = "(b) PR Activity by Contributor Type, Contribution Type, and Window",
       y = "Number of PRs",
       x = "Contributor Type",
       fill = "Contribution Type") +
  scale_x_discrete(labels = c("Staff" = "Staff", "External" = "External"))

# Print plot
pr_activity_plot

# Save as PNG
ggsave(filename = "github_plots/pr_activity.png", plot = pr_activity_plot,
       width = 10, height = 6, dpi = 300)
```
```{r r pr-contributor-contribution-merge-table, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(knitr)

# -----------------------
# Summarize PR counts for table
# -----------------------
pr_activity_table <- pr_all %>%
  group_by(Window, Merged, Contributor_Type, Contribution_Type) %>%
  summarise(PR_Count = n(), .groups = "drop") %>%
  mutate(Merged = factor(Merged,
                         levels = c(FALSE, TRUE),
                         labels = c("Not Merged", "Merged")))

# -----------------------
# Print table in Quarto-friendly format
# -----------------------
kable(pr_activity_table, 
      caption = "Table: PR counts by Merge Status, Contributor Type, Contribution Type, and Window",
      col.names = c("Window", "Merge Status", "Contributor Type", "Contribution Type", "Number of PRs"))
```


### Contributor Engagement

We explored if the number of new External contributors increased. In Window 1, there were 8 Staff and 18 External contributors. In Window 2, there were 6 Staff, 2 External (returning from Time Window 1), and 20 new External contributors. The number of contributors were therefore roughly similar between timepoints, but a large proportion of external contributors at Time Window 2 were new.
```{r contributor-engagement-plot, message=FALSE, warning=FALSE, echo=FALSE, fig.cap="Figure 2. Number of Staff and External contributors at Time window 1 and 2. For Time window 2 new contributors are also indicated with darker turquoise. Results show Merged and Not Merged contributions."}

# -----------------------
# Contributor engagement (for summary tables)
# -----------------------
contributor_engagement <- pr_all %>%
  group_by(Window, Contributor_Type) %>%
  summarise(
    Active_Contributors = n_distinct(Author),
    PRs_per_Contributor = n() / n_distinct(Author),
    New_Contributors = sum(!Author %in% pr_all$Author[pr_all$Window != Window])
  )

# 2) Active Contributors with External New highlighted in Window 2
# -----------------------
# Identify authors in Window 1
authors_w1 <- pr_all %>% filter(Window == "Window 1") %>% pull(Author) %>% unique()

# Label contributors for plotting
pr_all_plot <- pr_all %>%
  group_by(Window, Author) %>%
  summarise(.groups = "drop") %>%
  mutate(Plot_Type = case_when(
    Author %in% staff_authors ~ "Staff",
    Window == "Window 1" & !(Author %in% staff_authors) ~ "External",
    Window == "Window 2" & !(Author %in% staff_authors) & !(Author %in% authors_w1) ~ "External New",
    Window == "Window 2" & !(Author %in% staff_authors) & Author %in% authors_w1 ~ "External"
  ))

# Summarize counts for plotting
contrib_summary_plot <- pr_all_plot %>%
  group_by(Window, Plot_Type) %>%
  summarise(Active_Contributors = n(), .groups = "drop")

  
# Plot stacked bar
# Plot stacked bar
contributors_plot <- ggplot(contrib_summary_plot, aes(x = Window, y = Active_Contributors, fill = Plot_Type)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  scale_fill_manual(values = c("Staff" = "#f3a57f", 
                               "External" = "#d4f8fc", 
                               "External New" = "#7deaf6")) +
  labs(
    title = "Active Contributors by Window (Staff / External / External New)",
    y = "Active Contributors",        # Change Y axis label
    fill = "Contributor Type"         # Change legend title
  )

# Save and display
ggsave(filename = "github_plots/active_contributors.png", plot = contributors_plot, width = 6, height = 5, dpi = 300)
contributors_plot

# Summarize number of active contributors per window and type
contrib_summary_text <- contrib_summary_plot %>%
  group_by(Window, Plot_Type) %>%
  summarise(Count = sum(Active_Contributors), .groups = "drop") %>%
  tidyr::pivot_wider(names_from = Plot_Type, values_from = Count)

# Build a sentence using glue
summary_sentence <- glue(
  "In Window 1, there were {contrib_summary_text$Staff[contrib_summary_text$Window=='Window 1']} Staff and {contrib_summary_text$External[contrib_summary_text$Window=='Window 1']} External contributors. ",
  "In Window 2, there were {contrib_summary_text$Staff[contrib_summary_text$Window=='Window 2']} Staff, {contrib_summary_text$External[contrib_summary_text$Window=='Window 2']} External, ",
  "and {contrib_summary_text$`External New`[contrib_summary_text$Window=='Window 2']} new External contributors. The number of contributors were therefor roughly similar between timepoints, but a large proportion of external contributors at timepoint 2 were new."
)
```

`r summary_sentence`

## Supplementary Material 

To better understand the nature of engagement, we examined total lines changed per pull request.


```{r total-line-change-table, message=FALSE, warning=FALSE, echo=FALSE}
library(dplyr)
library(knitr)

# Summarise descriptives
summary_table <- pr_all %>%
  group_by(Window, Contributor_Type, Merged) %>%
  summarise(
    Count = n(),
    Mean = mean(`Total Lines Changed`, na.rm = TRUE),
    Median = median(`Total Lines Changed`, na.rm = TRUE),
    SD = sd(`Total Lines Changed`, na.rm = TRUE),
    Min = min(`Total Lines Changed`, na.rm = TRUE),
    Q1 = quantile(`Total Lines Changed`, 0.25, na.rm = TRUE),
    Q3 = quantile(`Total Lines Changed`, 0.75, na.rm = TRUE),
    Max = max(`Total Lines Changed`, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(Window, Contributor_Type, Merged)

# Print nicely
kable(summary_table, digits = 2, caption = "Descriptive statistics of Total Lines Changed by Window, Contributor Type, and Merge Status")

```

